---
title: "conversionsCleanExploreCompute v 1.2 - end of data"
author: "Steven Davenport"
date: "7/12/2018"
output: html_document
---

v 1.2 more stuff.  
+ removed "difference" scatterplots as they never showed any patterns.
+ disabled usable weight : weight ratio scatter plots

v l.1 (july 12):

+ Changed variables to analyze
  + removed redundancies (dropping weightdiff2 = childweight, parentdiff2 = parent_difference)
  + added uw_w_ratio (ratio of usableweight to weight)
  + added uwXw (usableweight * weight)
+ Changed observations to plot
  + Sample just N top pathways (set = 16)
  + from each, sample nObs (set = 2000 for big draws)
+ added/modified tables
  + sorted for clarity by child type, parent type
+ Added/modified plots
  + added histograms
  + fixed formatting for clarity, large values
+ Design changes
  + Moved parameters to top for easy changing
  + Streamlined data pipeline
  + improved outline
  
v 1.0 introduced the basic data pipeline.

```{r setup, include=TRUE, message=FALSE, warning=FALSE, echo = TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse); library(data.table); library(dtplyr); library(knitr)
conversions <- fread('../Kee Won/conversions.csv') %>%
  tail(1e6)
source("functions.R")

conversions <- conversions %>% mutate(date = as.Date(sessiontime, origin = '1970-01-01'))
```


## Set parameters

```{r}
nPath <- 25 # set number of pathways to look at
qTop <- .90 # set quantile for topcoding
nObs <- 400 # obs to sample per pathway group
options(scipen=7) # num sig digits (after this it will use scientific notation)

# Chart theme
chart_theme <- theme_minimal() + 
  theme(axis.text.x=element_text(angle = -15, hjust = 0)) # rotate text a bit
  
```

## Data clean/prep

### Select variables to analyze

Task: create a new var (if needed) for each metric in contention which you'll consider top-coding/exploring, i.e. parent_difference, (parent_start - parent_end), childweight, childusableweight. We will **enforce** parent_difference = parentweight_start - parentweight_end (KW says this only true 98% of the time).


```{r}
# narrow dataframe only to candidate weight columns to needed columns
conv <- conversions %>%
  mutate(parent_difference = parentweight_start - parentweight_end,
        # weightdiff2 = newweight - oldweight, # no longer calculated in v 1.1
        # parentdiff2 = parentweight_start - parentweight_end, # no longer calculated in v 1.1
        child_usableweight = as.numeric(child_usableweight),
        parent_difference = as.numeric(parent_difference),
        invtypeparent = getInvtype(inventorytype_parent),
        uw_w_ratio = child_usableweight / childweight,
        uwXw = child_usableweight * childweight,
        invtypechild = getInvtype(inventorytype),
        pathway = paste0(invtypeparent, " -> ", invtypechild)
        ) %>%
  select(inventoryid, 
         pathway, invtypeparent, invtypechild,
         difference, parent_difference, childweight, child_usableweight, uwXw, uw_w_ratio) %>%
  as.data.table
```

### Sample data from top pathways

Narrow for most common pathways only; sample equally for each. This will ensure that when we do results/scatters, we aren't overwhelmed or ending up with sparse data.


```{r}
# Find most common pathways
topPathways <- 
  conv[ , .N, pathway] %>% 
  arrange(-N) %>%
  head(nPath) %>%
  .$pathway

# Narrow the data to the top 16 pathways, getting nObs each
convPath16 <- conv[pathway %in% topPathways ,  # narrow
                   .SD[sample(x= .N, size=min(nObs, .N))], # sample nObs
                   by = pathway] # ... by pathway
```

### Re-shape for easy computations

```{r}
# make a "melted" (re-shaped) version for aggregations. ("M" stands for melted)
convPath16m <- (convPath16 %>% 
  gather(metric, value, difference:uw_w_ratio)) %>%
  as.data.table()

```

### Top-code by pathway quantiles

```{r, topCodingQuantiles}
# Get quantiles
pathQuants <- 
  convPath16m[ ,quantile(value, qTop, na.rm=T),
   by=.(invtypeparent, invtypechild, metric)] %>%
  rename(qTop = "V1")

# Make function to apply top-coding by pathway
topCode <- function(invtypeparentX, invtypechildX, metricX, valueX) {
  
  topCodeValue <- pathQuants[invtypeparent == invtypeparentX &
                               invtypechild == invtypechildX &
                               metric == metricX] %>%
    .$qTop
    
  return(ifelse(valueX > topCodeValue, topCodeValue, valueX))
  
}

# Apply top-coding function to data
convPath16m <- 
  convPath16m %>% 
  rowwise() %>% 
  mutate(valueTopCoded=topCode(invtypeparent, invtypechild, metric, value)) %>%
  as.data.table() 
```

## Univariate Analysis (pathway-metric)

### Modal values

```{r}
# Get modal value for each metric, by pathway
modes <- 
  convPath16m[ ,tail(sort(table(value)), 1),
   by=.(invtypeparent, invtypechild, metric)] %>%
  rename(mode = "V1")

modes %>%
  spread(metric, mode) %>% 
  arrange(invtypechild, invtypeparent) %>% # sort
  kable(caption="modal value by pathway, metric")
```

### Quantiles

```{r}
# Show quantile for each metric, by pathway
pathQuants %>%
  spread(metric, qTop) %>%
  arrange(invtypechild, invtypeparent) %>% # sort
  kable(caption=paste0(qTop*100, "th quantile by pathway, metric"))

```

### Histograms

This should help us interpret these units. We produce this for just four metrics (which I think matter).

```{r histograms, fig.width=20, fig.height=20, eval = F}
convPath16m %>% 
  filter(metric=='parent_difference') %>%
  ggplot(aes(x=valueTopCoded)) + 
  chart_theme + geom_histogram() + 
  facet_wrap(~pathway, scales='free') +
  labs(title='parent_difference')

convPath16m %>% 
  filter(metric=='child_usableweight') %>%
  ggplot(aes(x=valueTopCoded)) + 
  chart_theme + geom_histogram() + 
  facet_wrap(~pathway, scales='free') +
  labs(title='child_usableweight')

convPath16m %>% 
  filter(metric=='childweight') %>%
  ggplot(aes(x=valueTopCoded)) + 
  chart_theme + geom_histogram() + 
  facet_wrap(~pathway, scales='free') +
  labs(title='childweight')

convPath16m %>% 
  filter(metric=='uw_w_ratio') %>%
  ggplot(aes(x=valueTopCoded)) + 
  chart_theme + geom_histogram() + 
  facet_wrap(~pathway, scales='free') +
  labs(title='uw_w_ratio')

convPath16m %>% 
  filter(metric=='uwXw') %>%
  ggplot(aes(x=valueTopCoded)) + 
  chart_theme + geom_histogram() + 
  facet_wrap(~pathway, scales='free') +
  labs(title='uwXw (uw times w)')
```

## Bivariate (Scattter plots)

Scatter plots (w/ jitter/density for over-plotting); facet by each parent-child pathway, trading X/Y axes:

```{r}
# Review metrics; prep dataframes ready to plot diff combos
unique(convPath16m$metric)

### CHILDREN
# get child_usableweights
childuw <- convPath16m[metric=="child_usableweight"] %>%
  select(-metric) %>%
  rename(child_usableweight = valueTopCoded)

childw <- convPath16m[metric=="childweight"] %>%
  select(-metric) %>%
  rename(childweight = valueTopCoded)

### PARENTS
parentdiff <- convPath16m[metric=="parent_difference"] %>%
  select(-metric) %>%
  rename(parent_difference = valueTopCoded)

diff <- convPath16m[metric=="difference"] %>%
  select(-metric) %>%
  rename(difference = valueTopCoded)


### UW:W RATIO
uwwratio <- convPath16m[metric=="uw_w_ratio"] %>%
  select(-metric) %>%
  rename(uw_w_ratio = valueTopCoded)


### UW TIMES W
uwXw <- convPath16m[metric=="uwXw"] %>%
  select(-metric) %>%
  rename(uwXw = valueTopCoded)

```

```{r, include=F}
# PARENTS BELOW DROPPED FOR V1.1
# weightdiff2 <- convPath16m[metric=="weightdiff2"] %>%
#   select(-metric) %>%
#   rename(weightdiff2 = valueTopCoded)
# 
# parentdiff2 <- convPath16m[metric=="parentdiff2"] %>%
#   select(-metric) %>%
#   rename(parentdiff2 = valueTopCoded)
```


### Parent diff -> ...

#### parent diff (x) v child_usableweight (y)
```{r, fig.width=20, fig.height=20}
left_join(childuw %>% select(inventoryid, child_usableweight), 
          parentdiff, 
          by="inventoryid") %>%
  ggplot(aes(x=parent_difference, y=child_usableweight)) +
  chart_theme + geom_point(position='jitter', alpha=.1) +
  facet_wrap(~pathway, scales='free') +
  labs(title="parent diff (x) v child_usableweight (y)")
```

#### parent diff (x) v childweight (y)

```{r, fig.width=20, fig.height=20}
left_join(childw %>% select(inventoryid, childweight), 
          parentdiff, 
          by="inventoryid") %>%
  ggplot(aes(x=parent_difference, y=childweight)) +
  chart_theme + geom_point(position='jitter', alpha=.1) +
  facet_wrap(~pathway, scales='free') +
  labs(title="parent diff (x) v childweight (y)")
```

#### parent diff (x) v childweight * childusableweight (y)

```{r, fig.width=20, fig.height=20}
left_join(uwXw %>% select(inventoryid, uwXw), 
          parentdiff, 
          by="inventoryid") %>%
  ggplot(aes(x=parent_difference, y=uwXw)) +
  chart_theme + geom_point(position='jitter', alpha=.1) +
  facet_wrap(~pathway, scales='free') +
  labs(title="parent diff (x) v uwXw (y)")
```

<!-- ### Usablewweight : weight ratios (x) against child metrics (weight or usableweight) -->

<!-- #### UW:W ratio (y) -- child usable weight (x) -->
<!-- ```{r, fig.width=20, fig.height=20} -->
<!-- left_join(childuw %>% select(inventoryid, child_usableweight),  -->
<!--           uwwratio,  -->
<!--           by="inventoryid") %>% -->
<!--   ggplot(aes(y=uw_w_ratio, x=child_usableweight)) + -->
<!--   chart_theme + geom_point(position='jitter', alpha=.1) + -->
<!--   facet_wrap(~pathway, scales='free') + -->
<!--   labs(title="UW : W ratio (y) -- child_usableweight (x)") -->
<!-- ``` -->

<!-- #### UW:W ratio (y) -- child weight (x) -->

<!-- ```{r, fig.width=20, fig.height=20} -->
<!-- left_join(childw %>% select(inventoryid, childweight),  -->
<!--           uwwratio,  -->
<!--           by="inventoryid") %>% -->
<!--   ggplot(aes(y=uw_w_ratio, x=childweight)) + -->
<!--   chart_theme + geom_point(position='jitter', alpha=.1) + -->
<!--   facet_wrap(~pathway, scales='free') + -->
<!--   labs(title="UW : W ratio (y) -- childweight (x)") -->
<!-- ``` -->
