---
title: "conversionsCleanExploreCompute v 1.3 - end of data"
author: "Steven Davenport"
date: "`r format(Sys.time(), '%d %B, %Y %H:%M')`"
output: html_document
---

v 1.3:

+ focusing on calculating conversion ratios.

v 1.2 more stuff.  

+ removed "difference" scatterplots as they never showed any patterns.
+ disabled usable weight : weight ratio scatter plots

v l.1 (july 12):

+ Changed variables to analyze
  + removed redundancies (dropping weightdiff2 = childweight, parentdiff2 = parent_difference)
  + added uw_w_ratio (ratio of usableweight to weight)
  + added uwXw (usableweight * weight)
+ Changed observations to plot
  + Sample just N top pathways (set = 16)
  + from each, sample nObs (set = 2000 for big draws)
+ added/modified tables
  + sorted for clarity by child type, parent type
+ Added/modified plots
  + added histograms
  + fixed formatting for clarity, large values
+ Design changes
  + Moved parameters to top for easy changing
  + Streamlined data pipeline
  + improved outline
  
v 1.0 introduced the basic data pipeline.

```{r setup, include=TRUE, message=FALSE, warning=FALSE, echo = TRUE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)
library(tidyverse); library(data.table); library(dtplyr); library(knitr); library(lubridate)
source("functions.R")

conversions <- fread('../Kee Won/conversions.csv') %>%
  mutate(date = as_datetime(sessiontime, origin = '1970-01-01')) %>%
  dplyr::filter(year(date) == 2015)
```


## Set parameters

```{r, echo=TRUE}
lastN <- NA
nPath <- 40 # set number of pathways to look at
qTop <- .95 # set quantile for topcoding
nObs <- NA # obs to sample per pathway group
options(scipen=7) # num sig digits (after this it will use scientific notation)

# if you've got a LastN provided, just take that excerpt
if(!is.na(lastN)) {
  conversions <- conversions %>% tail(lastN)
}




# TODO:
# turn off proportional sampling, but rather restrict it to a smaller dataset?

# Chart theme
chart_theme <- theme_minimal() + 
  theme(axis.text.x=element_text(angle = -15, hjust = 0)) # rotate text a bit
  
```

## Data clean/prep

### Select variables to analyze

Task: create a new var (if needed) for each metric in contention which you'll consider top-coding/exploring, i.e. parent_difference, (parent_start - parent_end), childweight, childusableweight. We will **enforce** parent_difference = parentweight_start - parentweight_end (KW says this only true 98% of the time).


```{r}
# narrow dataframe only to candidate weight columns to needed columns
conv <- conversions %>%
  mutate(parent_difference = parentweight_start - parentweight_end,
        # weightdiff2 = newweight - oldweight, # no longer calculated in v 1.1
        # parentdiff2 = parentweight_start - parentweight_end, # no longer calculated in v 1.1
        child_usableweight = as.numeric(child_usableweight),
        parent_difference = as.numeric(parent_difference),
        invtypeparent = getInvtype(inventorytype_parent),
        
        # Tag with type of end product (retail v intermediate)
        endtype = getEndtype(inventorytype),
        
        # Calculate more stuff
        uw_w_ratio = child_usableweight / childweight,
        uwXw = child_usableweight * childweight,
        invtypechild = getInvtype(inventorytype),
        pathway = paste0(invtypeparent, " -> ", invtypechild)
        ) %>%
  select(inventoryid, 
         pathway, invtypeparent, invtypechild, endtype,
         difference, parent_difference, childweight, child_usableweight, uwXw, uw_w_ratio,
         date) %>%
  as.data.table
```

### Sample data from top pathways

Narrow for most common pathways only; sample equally for each. This will ensure that when we do results/scatters, we aren't overwhelmed or ending up with sparse data.


```{r}
# Find most common pathways
topPathways <- 
  conv[ , .N, pathway] %>% 
  arrange(-N) %>%
  head(nPath) %>%
  .$pathway


# Narrow the data to the top 16 pathways, getting nObs each
if(is.na(nObs)) {
  # if there's no value for nObs, don't sample
  convPath16 <- conv[pathway %in% topPathways]
} else {
  # if there is a value, take the sample accordingly
  convPath16 <- conv[pathway %in% topPathways ,  # narrow
                     .SD[sample(x= .N, size=min(nObs, .N))], # sample nObs
                     by = pathway] # ... by pathway
}

# Add indicator for intermediate child-producttype slope == 1
convPath16 <- convPath16 %>%
  mutate(intSlope1 = round(parent_difference / childweight, 2) == 1)
```


### Re-shape for easy computations

```{r}
# make a "melted" (re-shaped) version for aggregations. ("M" stands for melted)
convPath16m <- (convPath16 %>% 
  gather(metric, value, difference:uw_w_ratio)) %>%
  as.data.table()

```

### Top-code by pathway quantiles

```{r, topCodingQuantiles}
# Get quantiles
pathQuants <- 
  convPath16m[ , 
               quantile(value, qTop, na.rm=T),
               by=.(invtypeparent, invtypechild, metric, endtype)] %>%
  rename(qTop = "V1")

# Make function to apply top-coding by pathway
topCode <- function(invtypeparentX, invtypechildX, metricX, valueX) {
  
  topCodeValue <- pathQuants[invtypeparent == invtypeparentX &
                               invtypechild == invtypechildX &
                               metric == metricX] %>%
    .$qTop
    
  return(ifelse(valueX > topCodeValue, topCodeValue, valueX))
  
}

idTopCode <- function(invtypeparentX, invtypechildX, metricX, valueX) {
  
  topCodeValue <- pathQuants[invtypeparent == invtypeparentX &
                               invtypechild == invtypechildX &
                               metric == metricX] %>%
    .$qTop
    
  return(ifelse(valueX > topCodeValue, 'topCoded', 'real'))
  
}

# Apply top-coding function to data
convPath16m <- 
  convPath16m %>% 
  rowwise() %>% 
  mutate(valueTopCoded=topCode(invtypeparent, invtypechild, metric, value)) %>%
  as.data.table() 

convPath16m <- convPath16m %>%
  mutate(topCoded = (value != valueTopCoded))


```




```{r}
# Review metrics; prep dataframes ready to plot diff combos

### CHILDREN
# get child_usableweights
childuw <- convPath16m[metric=="child_usableweight"] %>%
  select(-metric) %>%
  rename(child_usableweight = valueTopCoded)

childw <- convPath16m[metric=="childweight"] %>%
  select(-metric) %>%
  rename(childweight = valueTopCoded)

### PARENTS
parentdiff <- convPath16m[metric=="parent_difference"] %>%
  select(-metric) %>%
  rename(parent_difference = valueTopCoded)

diff <- convPath16m[metric=="difference"] %>%
  select(-metric) %>%
  rename(difference = valueTopCoded)

```


## Ratios

```{r}
# Remove top-coded values
ratios <- left_join(childw %>% select(inventoryid, childweight, topCoded) , 
          parentdiff, 
          by="inventoryid") %>%
  mutate(slope = (parent_difference / childweight),
         remove = topCoded.x | topCoded.y | (round(slope, 1) %in% c(0, .5, 1, 2)))


# View edible retail products
ratiosEdible <- ratios %>%
  filter(endtype == "Retail",
         str_detect(invtypechild, "Edible")) %>%
  mutate(topCoded = topCoded.x | topCoded.y,
         slopeis1 = childweight == parent_difference,
         remove=topCoded |slopeis1)

# View non-edible retail products
ratiosNotEdible <- ratios %>%
  filter(endtype == "Retail",
         !str_detect(invtypechild, "Edible")) %>%
  mutate(topCoded = topCoded.x | topCoded.y,
         slopeis1 = childweight == parent_difference,
         remove=topCoded |slopeis1)

# Compute prevalence and ratios
prevalence <- ratios %>%
  group_by(invtypeparent, invtypechild, pathway, endtype) %>%
  summarise(pctslope1 = mean(slope==1),
            volOutAll = sum(parent_difference),
            volInAll = sum(childweight),
            volOut = sum(parent_difference[slope!=1 & !topCoded.x & !topCoded.y]),
            volIn = sum(childweight[slope!=1  & !topCoded.x & !topCoded.y])
            ) %>%
  mutate(ratio = volOut/volIn) %>%
  group_by(invtypeparent) %>%
  mutate(parentPathwayPct = volOut / sum(volOut)) %>%
  arrange(endtype, -invtypeparent, -ratio)

prevalence %>%
  select(pathway, endtype, volOut, volIn, ratio, parentPathwayPct, pctslope1) %>%
  knitr::kable(caption="Ratios and Pathway Percents (after removing identities, amounts >90th percentile)")

prevalence %>% write_csv(paste0("../output/pathways", " nObs",nObs, " q", qTop, " 2015.csv"))
```

### Path prevalence tables

TODO: reproduce these plots AFTER removing outliers from the dataset.
What percentage of each flower lot goes to each downstream product?

```{r}

convPath16[ str_detect(invtypeparent, "Lot") , # From flower lot
            .(parentdiff = sum(parent_difference)),
            .(invtypeparent, invtypechild, pathway)] %>%
  group_by(invtypeparent) %>%
  mutate(share = parentdiff/sum(parentdiff)) %>% 
  ggplot(aes(y=share, x=invtypechild)) + geom_col() + facet_wrap(~invtypeparent) +
  coord_flip() + 
  labs("Share from parent")

convPath16[ str_detect(invtypeparent, "Lot") , # From flower lot
            .(parentdiff = sum(parent_difference)),
            .(invtypeparent, invtypechild, pathway)] %>%
  group_by(invtypeparent) %>% 
  ggplot(aes(y=parentdiff, x=invtypechild)) + geom_col() + facet_wrap(~invtypeparent) +
  coord_flip() + 
  labs("Share from parent")

```


### Efficiency Tables

```{r}
# Calculate this but as a time series?
ratios[endtype == "Intermediate" & !remove, 
       .(convrateinv = (sum(childweight) / sum(parent_difference))^-1),
      .(pathway)] %>%
  arrange(-convrateinv) %>%
  knitr::kable(caption="Grams of Lots -> 1 gram Intermediate Product")

ratios[endtype == "Retail" & str_detect(invtypechild, "Edible"),
       .(convrateinv = (sum(childweight) / sum(parent_difference))^-1),
      .(pathway)] %>%
  arrange(-convrateinv) %>%
  knitr::kable(caption="Grams of intermediate product per Edible")

ratiosNotEdible[endtype == "Retail" & !str_detect(invtypechild, "Edible"),
       .(convrateinv = (sum(childweight) / sum(parent_difference))^-1),
      .(pathway)] %>%
  arrange(-convrateinv) %>%
  knitr::kable(caption="Grams of intermediate product per Retail Product")

```

