---
title: "conversionsCleanExploreCompute v 1.1"
author: "Steven Davenport"
date: "7/11/2018"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse); library(data.table); library(dtplyr); library(knitr)
conversions <- fread('../Kee Won/conversions.csv')
source("functions.R")
```


## data clean/prep

### narrow dataset w new variables

Task: create a new var (if needed) for each metric in contention which you'll consider top-coding/exploring, i.e. parent_difference, (parent_start - parent_end), childweight, childusableweight. Note a few new columns:

+ "weightdiff2" = newweight-oldweight
+ "parentdiff2" = parentweight_start - parentweight_end

```{r}
# narrow dataframe only to candidate weight columns to needed columns
conv <- conversions %>%
  select(inventoryid, 
         inventorytype_parent, inventorytype,
         oldweight, newweight, difference, parentweight_start, parentweight_end, parent_difference, childweight, child_usableweight) %>%
  mutate(weightdiff2 = newweight - oldweight,
         parentdiff2 = parentweight_start - parentweight_end,
         child_usableweight = as.numeric(child_usableweight),
         parent_difference = as.numeric(parent_difference),
         invtypeparent = getInvtype(inventorytype_parent),
         invtypechild = getInvtype(inventorytype)
         ) %>%
  select(-newweight,
         -oldweight,
         -parentweight_start, 
         -parentweight_end,
         -inventorytype_parent,
         -inventorytype)

```

## Make results tables

### Compute modal values by pathway, metric -> table

```{r}
# make a "melted" (re-shaped) version for aggregations.
convM <- (conv %>% 
  gather(metric, value, difference:parentdiff2)) %>%
  as.data.table()

# Get modal value for each metric, by pathway
modes <- 
  convM[ ,tail(sort(table(value)), 1),
   by=.(invtypeparent, invtypechild, metric)] %>%
  rename(mode = "V1")

modes %>%
  spread(metric, mode) %>%
  kable(caption="modal value by pathway, metric")
```

### Compute quantile by pathway.

```{r}
# Get 95th quantile for each metric, by pathway
pathQuants <- 
  convM[ ,quantile(value, .9, na.rm=T),
   by=.(invtypeparent, invtypechild, metric)] %>%
  rename(q90 = "V1")

pathQuants %>%
  spread(metric, q90) %>%
  kable(caption="90th quantile by pathway, metric")


```

### Top-code / remove values above the quantile.

```{r}
# Make function to apply top-coding by pathway
topCode <- function(invtypeparentX, invtypechildX, metricX, valueX) {
  
  topCodeValue <- pathQuants[invtypeparent == invtypeparentX &
                               invtypechild == invtypechildX &
                               metric == metricX] %>%
    .$q90

  # topCodeValue <- pathQuants$q90
    
  return(ifelse(valueX > topCodeValue, topCodeValue, valueX))
  
}
```

```{r}
convMSmall <- (conv %>% 
                 dplyr::sample_n(1e4) %>%
  gather(metric, value, difference:parentdiff2)) %>%
  as.data.table()


# Apply top-coding function to random sample (for speed)
convMTopCoded <-
  convMSmall %>% 
  rowwise() %>%
  mutate(valueTopCoded=topCode(invtypeparent, invtypechild, metric, value))

# Compute "pathway" variable
convMTopCoded <- convMTopCoded %>%
  as.data.table() %>%
  mutate(pathway = paste0(invtypeparent, " -> ", invtypechild)) 

# Find most common pathways
topPathways <- 
  convMTopCoded[ , .N, pathway] %>% 
  arrange(-N) %>%
  head(9) %>%
  .$pathway

# Filter data to most common pathways
convMTopCodedCommon <- convMTopCoded[pathway %in% topPathways]

```


## Make Charts

Scatter plots (w/ jitter/density for over-plotting); facet by each parent-child pathway, trading X/Y axes:

```{r}
# Review metrics; prep dataframes ready to plot diff combos
unique(convMTopCodedCommon$metric)


### CHILDREN
# get child_usableweights
childuw <- convMTopCodedCommon[metric=="child_usableweight"] %>%
  select(-metric) %>%
  rename(child_usableweight = valueTopCoded)

childw <- convMTopCodedCommon[metric=="childweight"] %>%
  select(-metric) %>%
  rename(childweight = valueTopCoded)



### PARENTS

parentdiff <- convMTopCodedCommon[metric=="parent_difference"] %>%
  select(-metric) %>%
  rename(parent_difference = valueTopCoded)

weightdiff2 <- convMTopCodedCommon[metric=="weightdiff2"] %>%
  select(-metric) %>%
  rename(weightdiff2 = valueTopCoded)

parentdiff2 <- convMTopCodedCommon[metric=="parentdiff2"] %>%
  select(-metric) %>%
  rename(parentdiff2 = valueTopCoded)

diff <- convMTopCodedCommon[metric=="difference"] %>%
  select(-metric) %>%
  rename(difference = valueTopCoded)

```


### Parent diff -> ...

#### parent diff (x) v child_usableweight (y)
```{r, fig.width=8, fig.height=8}
left_join(childuw %>% select(inventoryid, child_usableweight), 
          parentdiff, 
          by="inventoryid") %>%
  ggplot(aes(x=parent_difference, y=child_usableweight)) +
  geom_point(position='jitter') +
  facet_wrap(~pathway, scales='free') +
  labs(title="parent diff (x) v child_usableweight (y)")
```

#### parent diff (x) v childweight (y)

```{r, fig.width=8, fig.height=8}
left_join(childw %>% select(inventoryid, childweight), 
          parentdiff, 
          by="inventoryid") %>%
  ggplot(aes(x=parent_difference, y=childweight)) +
  geom_point(position='jitter') +
  facet_wrap(~pathway, scales='free') +
  labs(title="parent diff (x) v childeweight (y)")
```


### Parent diff2 (parent_end - parent_start) -> ...

#### parent diff2 (x) v child_usableweight (y)
```{r, fig.width=8, fig.height=8}
left_join(childuw %>% select(inventoryid, child_usableweight), 
          parentdiff2, 
          by="inventoryid") %>%
  ggplot(aes(x=parentdiff2, y=child_usableweight)) +
  geom_point(position='jitter') +
  facet_wrap(~pathway, scales='free') +
  labs(title="parent diff2 (x) v child_usableweight (y)")
```

#### parent diff2 (x) v childweight (y)

```{r, fig.width=8, fig.height=8}
left_join(childw %>% select(inventoryid, childweight), 
          parentdiff2, 
          by="inventoryid") %>%
  ggplot(aes(x=parentdiff2, y=childweight)) +
  geom_point(position='jitter') +
  facet_wrap(~pathway, scales='free') +
  labs(title="parent diff2 (x) v childweight (y)")
```


### "Difference" (parent_end - parent_start) -> ...

#### "Difference" (x) v child_usableweight (y)
```{r, fig.width=8, fig.height=8}
left_join(childuw %>% select(inventoryid, child_usableweight), 
          diff, 
          by="inventoryid") %>%
  ggplot(aes(x=difference, y=child_usableweight)) +
  geom_point(position='jitter') +
  facet_wrap(~pathway, scales='free') +
  labs(title="diff (x) v child_usableweight (y)")
```

#### "Difference" (x) v childweight (y)

```{r, fig.width=8, fig.height=8}
left_join(childw %>% select(inventoryid, childweight), 
          diff, 
          by="inventoryid") %>%
  ggplot(aes(x=difference, y=childweight)) +
  geom_point(position='jitter') +
  facet_wrap(~pathway, scales='free') +
  labs(title="diff (x) v childweight (y)")
```


### "weightdiff2" (newweight - oldweight) -> ...

#### "weightdiff2" (x) v child_usableweight (y)
```{r, fig.width=8, fig.height=8}
left_join(childuw %>% select(inventoryid, child_usableweight), 
          weightdiff2, 
          by="inventoryid") %>%
  ggplot(aes(x=weightdiff2, y=child_usableweight)) +
  geom_point(position='jitter') +
  facet_wrap(~pathway, scales='free') +
  labs(title="weightdiff2 (x) v child_usableweight (y)")
```

#### "weightdiff2" (x) v childweight (y)

```{r, fig.width=8, fig.height=8}
left_join(childw %>% select(inventoryid, childweight), 
          weightdiff2, 
          by="inventoryid") %>%
  ggplot(aes(x=weightdiff2, y=childweight)) +
  geom_point(position='jitter') +
  facet_wrap(~pathway, scales='free') +
  labs(title="weightdiff2 (x) v childweight (y)")
```
