---
title: "Explore Traceability"
author: "Steven Davenport"
date: "7/2/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      # Graphic output
                      fig.width = 8, fig.align='center')
library(tidyverse)
library(knitr)
source("functions.r")
```

The inventoryconversions data is useful, but aggregations of it seem to produce total nonsense. This is likely due to some extreme outliers. Below we will use a method to find reasonable top-censor cutoffs. This will tabulate licensee-inventorytype maximums, take the quantile at a certain value, and then use these values to establish a top-censor value.

```{r}
CensorMaxQuantile <- .8
CensorMaxQuantile
```

**In this iteration, the percentile thresshold is `r CensorMaxQuantile`**

# inventoryconversions: find top-censor thresholds.

## parentwt
```{r invconv_parentwt}
# QUERY:
# -- Explore cutoff for top-censoring parent-/child-(usable)weight
# -- Compare maximum values across licensees/ inventorytypes
# 
# SELECT location, inventorytype_parent,
# max(parent_difference) as parentwt,
# --max(childweight) as childwt,
# --max(child_usableweight) as childuwt
# FROM [rand-systems:full_WA_data.biotrackthc_inventoryconversions]
# GROUP BY location, inventorytype_parent;
parentwt <- read_csv("../gqoutput/results-20180702-184647.csv") %>%
  mutate(invtype = getInvtype(inventorytype_parent),
         parentwt = as.numeric(parentwt))

# Let's take the 95th percentile of licensee-inventorytype parentwt maximums
parentwtmax95 <- with(parentwt, 
                      tapply(parentwt, 
                             inventorytype_parent, 
                             function(x) quantile(x, CensorMaxQuantile, na.rm=T)))  %>% 
  round(-2)# rounded to nearest 10.

ggplot(parentwt,
      aes(x=parentwt)) + geom_histogram() + facet_wrap(~invtype, scales = 'free') +
  labs(title="parentwt: Biggest value observed by licensee (dirty data)",
       subtitle="Use this to inform choice of top-censoring value in dataset")
```

Below we show the 95th percentile of licensee-inventorytype parentwt maximums
```{r}

parentwtmax95 %>% data.frame %>%
  `colnames<-`('value') %>%
  mutate(invtype = getInvtype(names(parentwtmax95)),
         invnum = names(parentwtmax95)) %>% 
  arrange(-value) %>%
  kable(caption="parentwt: Proposed Top-Censoring Values for Inventorytype")
  
```

## childwt
```{r invconv_childwt}
# QUERY:
# -- Explore cutoff for top-censoring parent-/child-(usable)weight
# -- Compare maximum values across licensees/ inventorytypes
# SELECT location, inventorytype,
# max(childweight) as childwt,
# --max(child_usableweight) as childuwt
# FROM [rand-systems:full_WA_data.biotrackthc_inventoryconversions]
# GROUP BY location, inventorytype;

# Load the data
childwt <- read_csv("../gqoutput/results-20180702-190735.csv") %>%
  mutate(invtype = getInvtype(inventorytype),
         childuwt = as.numeric(childuwt))

# Let's take the 95th percentile of licensee-inventorytype parentwt maximums
childwtmax95 <- with(childwt, 
                      tapply(childwt, 
                             inventorytype, 
                             function(x) quantile(x, CensorMaxQuantile, na.rm=T)))  %>% 
  round(-2)# rounded to nearest 10.

ggplot(childwt,
      aes(x=childwt)) + geom_histogram() + facet_wrap(~invtype, scales = 'free') +
  labs(title="childwt: Biggest value observed by licensee (dirty data)",
       subtitle="Use this to inform choice of top-censoring value in dataset")

## Find 95th percentile of max

childwtmax95 %>% data.frame %>%
  `colnames<-`('value') %>%
  mutate(invtype = getInvtype(names(childwtmax95)),
         invnum = names(childwtmax95)) %>% 
  arrange(-value) %>% 
  kable(caption="childwt: Proposed Top-Censoring Values for Inventorytype")

```

### Child usableweight
```{r}
childuwtmax95 <- with(childwt, 
                      tapply(childuwt, 
                             inventorytype, 
                             function(x) quantile(x, CensorMaxQuantile, na.rm=T)))  %>% 
  round(-2)# rounded to nearest 10.


ggplot(childwt,
      aes(x=childuwt)) + geom_histogram() + facet_wrap(~invtype, scales = 'free') +
  labs(title="childusablewt: Biggest value observed by licensee (dirty data)",
       subtitle="Use this to inform choice of top-censoring value in dataset")

## Find 95th percentile of max
childuwtmax95 %>% data.frame %>%
  `colnames<-`('value') %>%
  mutate(invtype = getInvtype(names(childuwtmax95)),
         invnum = names(childuwtmax95)) %>% 
  arrange(-value) %>% 
  kable(caption="childusablewt: Proposed Top-Censoring Values for Inventorytype")

```
