---
title: "Reporting Harvest Statistics for Washington State"
author: "Kee Won Song"
date: "`r format(Sys.time(), '%B %d, %Y (%H:%M)')`"
output: html_document
---


## Introduction
This document will calculate statistics from the table named 'plantderivatives' in the Washington State Marijuana Traceability data set.  For most plants, a wet weight and a dry weight are reported.  For plants that are missing either a wet weight or a dry weight, the missing weight was imputed.  The conversion ratio for each producer was calculated for all plants that reported a wet and dry weight.  This ratio was used to impute missing weights.  Conversion ratios were constrained to fall between 0.14 and 0.35, a range that was guided by existing literature on yield.  Dry weights greater than 1.5 kg (3.3 lbs) were removed from the data set (11,550 plants or 0.2%).  This cutoff point was guided by the literature. 


```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      # Graphic output
                      fig.width = 8, fig.align='center')

library(dplyr)
library(ggplot2)
library(tidyr)
library(readr)
library(lubridate)
library(forcats)
library(ggthemes)
library(knitr)

#Set scipen
options(scipen = 100)

```

 
 
```{r}

##Import plant statistics
plant_stats <- read.csv('~/Documents/Cannabis Study/Final Analysis/plant_stats_distinct_location.csv')


```



```{r}

#Remove rows where dry weight and wet weight are both zero: 56,335 rows
plant_stats <- filter(plant_stats, wet_weight > 0 | dry_weight > 0)

#Create a data set for plants that were measured at different locations
plantid_dup <- plant_stats[which(duplicated(plant_stats$plantid)),]
aggregate_plants <- filter(plant_stats, (plantid %in% plantid_dup$plantid) & plantid != 'NULL')

#Add new dry weight column
aggregate_plants <- aggregate_plants %>% group_by(plantid) %>% mutate(sum_dry_weight = sum(dry_weight))
aggregate_plants <- filter(aggregate_plants, dry_weight == 0)
aggregate_plants <- select(aggregate_plants, -dry_weight)

colnames(aggregate_plants) <- c("location", "locationtype", "plantid","sessiontime", "wet_weight", "opm_weight", "dry_weight")


#Now remove all those plants from the original data set and rbind the aggregated plants back in
plant_stats <- filter(plant_stats, !plantid %in% aggregate_plants$plantid)
#Now combine the two data sets
plant_stats <- plyr::rbind.fill(plant_stats, aggregate_plants)

#Convert time stamp to a datetime object for year and month
plant_stats$date <- as_datetime(plant_stats$sessiontime)
plant_stats$year <- year(as_datetime(plant_stats$sessiontime))
plant_stats$month <- month(as_datetime(plant_stats$sessiontime))

```





```{r}


#Remove plants with a dry weight that is unbelievable.
plant_stats <- filter(plant_stats, wet_weight < 10500, dry_weight < 1500)

#Subset for all non-zero rows
conversion <- filter(plant_stats, dry_weight > 0 & wet_weight > 0) %>% group_by(location) %>%
                summarize(ratio = sum(dry_weight) / sum(wet_weight))

#Impose lower and upper bounds on ratio of dry to wet
conversion$ratio[which(conversion$ratio < .14)] <- .14
conversion$ratio[which(conversion$ratio > .35)] <- .35

#Merge the conversion ratios into the data set
plant_stats <- merge(plant_stats, conversion, by = 'location', all.x = T)

#Use upper and lower bounds for conversions where there are no values to calculate the actual ratio
plant_stats$ratio[which(plant_stats$wet_weight == 0 & is.na(plant_stats$ratio))] <- .35
plant_stats$ratio[which(plant_stats$dry_weight == 0 & is.na(plant_stats$ratio))] <- .14

#Impute the weights
plant_stats$dry_weight[which(plant_stats$dry_weight == 0)] <- plant_stats$wet_weight[which(plant_stats$dry_weight == 0)] * plant_stats$ratio[which(plant_stats$dry_weight == 0)]
plant_stats$wet_weight[which(plant_stats$wet_weight == 0)] <- plant_stats$dry_weight[which(plant_stats$wet_weight == 0)] * (1 / plant_stats$ratio[which(plant_stats$wet_weight == 0)])

```


```{r}

#Create a monthly index
plant_stats$month_index <- 0
plant_stats$month_index[which(plant_stats$year == 2014)] <- plant_stats$month[which(plant_stats$year == 2014)]
plant_stats$month_index[which(plant_stats$year == 2015)] <- plant_stats$month[which(plant_stats$year == 2015)] + 12
plant_stats$month_index[which(plant_stats$year == 2016)] <- plant_stats$month[which(plant_stats$year == 2016)] + 24
plant_stats$month_index[which(plant_stats$year == 2017)] <- plant_stats$month[which(plant_stats$year == 2017)] + 36

#Filter out plants that are from December 2017, because this is an error
plant_stats <- filter(plant_stats, month_index < 47)

```


```{r}

#Calculate the harvest statistics for each year
harvest_stats <- plant_stats %>% group_by(year) %>% summarize(plants = length(plantid), wet_weight = sum(wet_weight),
                                                              dry_weight = sum(dry_weight),opm_weight = sum(opm_weight),
                                                              per_plant = dry_weight / length(plantid))

```



```{r}


#Calculate the ratio of production in the last two months of 2016
plant_stats_ratio <- filter(plant_stats, year %in% c(2016, 2017))

#Calculate the proportion of the year's weight that came in the last two months
oct_total <- filter(plant_stats_ratio, month <= 10, year == 2016) %>% group_by(location) %>% summarize(oct_wet_total = sum(wet_weight), oct_dry_total = sum(dry_weight))
dec_total <- filter(plant_stats_ratio, month > 10, year == 2016) %>% group_by(location) %>% summarize(dec_wet_total = sum(wet_weight), dec_dry_total = sum(dry_weight))

ratio_2016 <- merge(oct_total, dec_total, by = 'location', all = T)
ratio_2016[is.na(ratio_2016)] <- 1

ratio_2016$wet_ratio <- ratio_2016$dec_wet_total / ratio_2016$oct_wet_total
ratio_2016$dry_ratio <- ratio_2016$dec_dry_total / ratio_2016$oct_dry_total
ratio_2016$wet_ratio[which(ratio_2016$wet_ratio < .15/.85)] <- .15/.85
ratio_2016$wet_ratio[which(ratio_2016$wet_ratio > .4/.6)] <- .4/.6
ratio_2016$dry_ratio[which(ratio_2016$dry_ratio < .15/.85)] <- .15/.85
ratio_2016$dry_ratio[which(ratio_2016$dry_ratio > .4/.6)] <- .4/.6

#Merge the ratios into the plants data set
plant_stats_2017 <- merge(filter(plant_stats, year == 2017), select(ratio_2016, location, wet_ratio, dry_ratio), by = 'location')

```



```{r}

#Calculate 2017 projections
projection_2017 <- plant_stats_2017 %>% group_by(location, wet_ratio, dry_ratio) %>%
                          summarize(n_plants = length(plantid), wet_weight = sum(wet_weight), 
                                    dry_weight = sum(dry_weight))

#The proportion of production from 2016 that occurred in the last two months of the year
projection_2017$wet_weight <- projection_2017$wet_weight * (1 + projection_2017$wet_ratio)
projection_2017$dry_weight <- projection_2017$dry_weight * (1 + projection_2017$dry_ratio)

```


```{r}

#Build the row of harvest stats for the 2017 projections
projection_2017 <- projection_2017 %>% group_by() %>% summarize(year = '2017 proj.', plants = 2108767 * 7/6, wet_weight = sum(wet_weight), dry_weight = sum(dry_weight), opm_weight = 86711469 * 7/6, per_plant = dry_weight / plants)

#Add the new row to harvest stats table
harvest_stats <- rbind(harvest_stats, projection_2017)

```



```{r}

#Write ouput
write.csv(harvest_stats, '~/harvest stats.csv', row.names = FALSE)

```


```{r}

#Display table
kable(harvest_stats, digits = c(rep(0,5), 1), col.names = c("Year", "No. Plants", "Wet weight (g)", "Dry Weight (g)", "OPM Weight (g)", "Yield per Plant (g)"), align = 'c')


```

