---
title: "Estimate mgTHC (Edible and non-Edible)"
author: "Steven Davenport"
date: "`r format(Sys.time(), '%d %B, %Y %H:%M(%S)')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
---

This comes from a document originally written by Anhvinh Doanvo. It will impute edible potency in the style used by the CMU team.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, messages=FALSE, warnings = FALSE, warning = FALSE)
options(scipen = 7)
library(plyr); library(tidyverse)
library(knitr); library(glmnet); library(randomForest); library(tm)
library(qdap); library(ranger)
source("CMU_code_share_av.R") #Import "search_productname(arg)", where arg = inventory product name
```

# Parameters

This informs us about the time frame we are looking at.

```{r parameters, echo = TRUE}
# scaleability parameter; sets sample size, # RF trees, and # PCA
divisor <- 10

# Export results to CSV?
export_estimates <- FALSE # Enable to write CSV for THC estimates
export_filename <- "../data/THC_estimates_nocbddominantedibles.csv"

# Import random sample of edibles table
edibles <- read.csv("../data/ediblesAlltimeSample200k.csv")  # Load dataset: all time

# Hard-coded data on all-time row counts from SQL table (not just what is imported to R)
n_solid_rows <- 8487415 # 22 # verified sept 24
n_liquid_rows <- 2150470 # 23 # verified sept 24
n_edible_rows <-  n_solid_rows + n_liquid_rows
```

```{r other_parameters, echo = FALSE}
rows_sampled_sql <- nrow(edibles) # number of rows in our SQL parameter
n_sample_obs <- rows_sampled_sql / divisor # number of obs to sample from all edibles from SQL export

message(paste0("# Edible rows sampled from SQL database: ", rows_sampled_sql))
```

# Prep Census Data

Census data was downloaded from [this source](https://www.census.gov/geo/maps-data/data/tiger-data.html). I selected the 2015 "detailed tables" for the Washington State block group. The "X19_INCOME" table was table-joined to the "ACS_2015_5YR_BG_53_WASHINGTON" shapefile using X19's GEOID and ACS's GEOID_Data fields. Furthermore, the stores identified in the biotrackthc_locations table were geocoded using their latitude and longitudinal coordinates.

These stores were spatial-joined to their associated census tract to relate them to demographic data of their surrounding region. Using this data, an 'income index' was calculated for each store by compositing counts of individuals in each income bracket per store in each census tract. The data coding information sourced from the American Community Survey is in a code chunk in this rmd file.

```{r calculate income index, echo = F}
censusdata <- read.csv("../data/biotrackthc_locations_cenus_joined.csv") # Steve's directory

# This calculates average income by census tract
censusdata$avgincome <- (censusdata$X19_INCOME_B19001e2 * 5000 +
censusdata$X19_INCOME_B19001e3 * 12500 +
censusdata$X19_INCOME_B19001e4 * 17500 +
censusdata$X19_INCOME_B19001e5 * 22500 +
censusdata$X19_INCOME_B19001e6 * 27500 +
censusdata$X19_INCOME_B19001e7 * 32500 +
censusdata$X19_INCOME_B19001e8 * 37500 +
censusdata$X19_INCOME_B19001e9 * 42500 +
censusdata$X19_INCOME_B19001e10 * 47500 +
censusdata$X19_INCOME_B19001e11 * 55000 +
censusdata$X19_INCOME_B19001e12 * 67500 +
censusdata$X19_INCOME_B19001e13 * 87500 +
censusdata$X19_INCOME_B19001e14 * 112500 +
censusdata$X19_INCOME_B19001e15 * 137500 +
censusdata$X19_INCOME_B19001e16 * 175000) / (censusdata$X19_INCOME_B19001e2 +
censusdata$X19_INCOME_B19001e3 +
censusdata$X19_INCOME_B19001e4 +
censusdata$X19_INCOME_B19001e5 +
censusdata$X19_INCOME_B19001e6 +
censusdata$X19_INCOME_B19001e7 +
censusdata$X19_INCOME_B19001e8 +
censusdata$X19_INCOME_B19001e9 +
censusdata$X19_INCOME_B19001e10 +
censusdata$X19_INCOME_B19001e11 +
censusdata$X19_INCOME_B19001e12 +
censusdata$X19_INCOME_B19001e13 +
censusdata$X19_INCOME_B19001e14 +
censusdata$X19_INCOME_B19001e15 +
censusdata$X19_INCOME_B19001e16) #for lower incomes, get average estimated

# This gets percent of population in top bracket
censusdata$pcttopbracket <- censusdata$X19_INCOME_B19001e17 / (censusdata$X19_INCOME_B19001e2 +
censusdata$X19_INCOME_B19001e3 +
censusdata$X19_INCOME_B19001e4 +
censusdata$X19_INCOME_B19001e5 +
censusdata$X19_INCOME_B19001e6 +
censusdata$X19_INCOME_B19001e7 +
censusdata$X19_INCOME_B19001e8 +
censusdata$X19_INCOME_B19001e9 +
censusdata$X19_INCOME_B19001e10 +
censusdata$X19_INCOME_B19001e11 +
censusdata$X19_INCOME_B19001e12 +
censusdata$X19_INCOME_B19001e13 +
censusdata$X19_INCOME_B19001e14 +
censusdata$X19_INCOME_B19001e15 +
censusdata$X19_INCOME_B19001e16 +
censusdata$X19_INCOME_B19001e17) # for very high-income indivduals, just grab percentage in that bracket

store_incomes <- data.frame(store_loc = censusdata$ID,
                           avgincome = censusdata$avgincome,
                           pcttopbracket = censusdata$pcttopbracket)

# de-duplicate; take average for stores w multiple locations
store_incomes <- store_incomes[!duplicated(store_incomes),]
store_avg_income <- aggregate(avgincome ~ store_loc, 
                          data = store_incomes,
                          FUN = mean)
store_top_pct <- aggregate(pcttopbracket ~ store_loc, 
                          data = store_incomes,
                          FUN = mean)


store_incomes <- merge(x = store_avg_income, y = store_top_pct, by = "store_loc")  # NOT inv_location
rm(store_avg_income)
rm(store_top_pct)
##NEED TO CHECK THIS WORK

```

# Edibles

## Prep/Describe Edible Data

```{r prep edibles data}
# Load random sample of edible observations
edibles <- edibles %>%
  
  # Sample for computational speed
  dplyr::sample_n(n_sample_obs) %>%
  
  # Parse saletime and interaction term for price * saletime
  mutate(date = as.POSIXct(as.character(sale_time), origin='1970-01-01'),
         sale_time = as.numeric(as.POSIXct(as.character(sale_time))),
         pricetime = (sale_time - mean(sale_time)) * price_x,
         year = lubridate::year(date),
         month = lubridate::month(date),
         invtype = ifelse(inventorytype==22, "Solid Edible", "Liquid Edible"),
         
         # Add mgTHC estimates
         mgTHC = (search_productname(inv_productname)$mg_text_max %>% 
                    # topcode @ 500mg THC per unit (medical market maximum)
                    ifelse(. > 500, 500, .) * 
                    # multiply by # units
                    weight),
         
         # Top-code the THC/CBD fields
         # Note: these vars aren't used in models, just to determine THC or CBD-dominant
         Potency_THC = ifelse(Potency_THC > 100, 100, Potency_THC),
         Potency_CBD = ifelse(Potency_CBD > 100, 100, Potency_CBD)) %>%
  
  # merge on census data (store income)
  left_join(store_incomes)

# Basic summary stats
edibles %>% 
  group_by(year) %>%
  summarise(n_rows = n(),
            weight = sum(weight),
            THC_value_mean = mean(Potency_THC, na.rm=T),
            CBD_value_mean = mean(Potency_CBD, na.rm=T),
            price_x = mean(price_x, na.rm=T)) %>%
  kable(caption="Summary info", digits=2)

# Validate different types of missingness.
edibles %>% 
  group_by(year) %>%
  summarise(date_na = sum(is.na(date)),
            THC_na = sum(is.na(Potency_THC)),
            CBD_na = sum(is.na(Potency_CBD)),
            weight_na = sum(is.na(weight)),
            label_na = sum(is.na(inv_productname) | inv_productname=="")) %>%
  kable(caption="Missingness in the sample dataset", digits=2)

```

## ID THC v CBD dominant products

```{r THCvCBD}
# Let us define CBD products if CBD > THC or label contains THC; otherwise, it will be THC
edibles <- edibles %>%
  mutate(dominant_unknown = is.na(Potency_CBD) & is.na(Potency_THC) & !str_detect(inv_productname, '(?i)CBD'),
         dominant = case_when(dominant_unknown ~ "THC",
                              str_detect(inv_productname, "(?i)CBD") | Potency_CBD > Potency_THC ~ "CBD",
                              TRUE ~ "THC"))

# Validate THC v CBD products
edibles %>% 
  filter(invtype=="Liquid Edible") %>%
  group_by(year) %>%
  summarise(labeled_CBD = sum(str_detect(inv_productname, "(?i)CBD")),
            cbd_exceeds_thc = sum(Potency_CBD > Potency_THC, na.rm=T),
            `categorizedCBD(either)` = sum(str_detect(inv_productname, "(?i)CBD") | (Potency_CBD > Potency_THC), na.rm=T),
            categorizedTHC = sum(dominant=='THC'),
            total = n(),
            uncategorized = total-categorizedTHC-`categorizedCBD(either)`,
            pct_THC = categorizedTHC / total
            ) %>%
  kable(caption="Liquid edibles: THC v CBD dominant products", digits=2)

# Validate THC v CBD products
edibles %>% 
  filter(invtype=="Solid Edible") %>%
  group_by(year) %>%
  summarise(labeled_CBD = sum(str_detect(inv_productname, "(?i)CBD")),
            cbd_exceeds_thc = sum(Potency_CBD > Potency_THC, na.rm=T),
            `categorizedCBD(either)` = sum(str_detect(inv_productname, "(?i)CBD") | (Potency_CBD > Potency_THC), na.rm=T),
            categorizedTHC = sum(dominant=='THC'),
            total = n(),
            uncategorized = total-categorizedTHC-`categorizedCBD(either)`,
            pct_THC = categorizedTHC / total
            ) %>%
  kable(caption="Solid Edibles: THC v CBD dominant products", digits=2)


# Point estimate for % of liquid/solid that are THC or CBD-dominant
thc_cbd_prevalence <- edibles %>% 
  group_by(invtype) %>%
  summarise(`categorizedCBD(either)` = sum(str_detect(inv_productname, "(?i)CBD") | (Potency_CBD > Potency_THC), na.rm=T),
            categorizedTHC = sum(dominant=='THC'),
            total = n(),
            pct_THC = categorizedTHC / total
            )

thc_cbd_prevalence %>%
  kable(caption="Solid Edibles: THC v CBD dominant products", digits=2)


# Save constants for scaling up the random forest results
liq_pct_THC <- thc_cbd_prevalence %>%
  filter(invtype=="Liquid Edible") %>% .$pct_THC

sol_pct_THC <- thc_cbd_prevalence %>%
  filter(invtype=="Solid Edible") %>% .$pct_THC

# THC v CBD breakdown, liquid v solids
edibles %>% 
  filter(invtype=="Solid Edible") %>%
  group_by(year, dominant) %>%
  summarise(num =n(),
            weight = sum(weight),
            # THC_value_mean = mean(Potency_THC, na.rm=T),
            # CBD_value_mean = mean(Potency_CBD, na.rm=T), 
            mg_mean = mean(mgTHC, na.rm=T),
            assumed_THC = sum(dominant_unknown)
            )  %>%
  kable(caption="Solid edibles: THC v CBD products", digits=2)


edibles %>% 
  filter(invtype=="Liquid Edible") %>%
  group_by(year, dominant) %>%
  summarise(num =n(),
            weight = sum(weight),
            # THC_value_mean = mean(Potency_THC, na.rm=T),
            # CBD_value_mean = mean(Potency_CBD, na.rm=T), 
            mg_mean = mean(mgTHC, na.rm=T),
            assumed_THC = sum(dominant_unknown)
            )  %>%
  kable(caption="Liquid edibles: THC v CBD products", digits=2)


```

```{r}

```

```{r}

message(paste0("rows in edible dataset before filtering for thc/inventorytype/sale time: ", nrow(edibles))) # check num rows
# edibles <- edibles %>%
#   # Remove rows with blank THC/date/inventorytype
#   filter(!is.na(Potency_THC),
#          !is.na(sale_time),
#          !is.na(inventorytype)) 
message(paste0("rows in edible dataset AFTER filtering for thc/inventorytype/sale time: ", nrow(edibles))) # check num rows

```


```{r, eval = F}
edibles %>% filter(dominant=='THC',
                   year==2015,
                   invtype=="Solid Edible",
                   !is.na(Potency_CBD)) 
```

## Plot mgTHC/CBD and Price

```{r plot, fig.height=2}
# hist -> 500mg
ggplot(edibles %>% filter(dominant=='THC'), aes(x = mgTHC)) +
  geom_histogram() +
  facet_grid(.~ invtype) + xlim(c(0, 500)) +
  labs(title="Distribution mgTHC")

ggplot(edibles %>% filter(dominant=='CBD'), aes(x = mgTHC)) +
  geom_histogram() +
  facet_grid(.~ invtype) + xlim(c(0, 500)) +
  labs(title="CBD: Distribution mg", x='CBD')

# hist -> 100mg (where most data are)
ggplot(edibles %>% filter(dominant=='THC'), aes(x = mgTHC)) +
  geom_histogram() +
  facet_grid(.~ invtype) + xlim(c(0, 100)) +
  labs(title="Distribution mgTHC")

ggplot(edibles %>% filter(dominant=='CBD'), aes(x = mgTHC)) +
  geom_histogram() +
  facet_grid(.~ invtype) + xlim(c(0, 100)) +
  labs(title="CBD: Distribution mg", x='CBD')

# relationship w average price
ggplot(edibles %>% filter(dominant=='THC'), aes(y = price_x, x = mgTHC)) +
  geom_point(alpha = 0.1) +
  facet_grid(.~ invtype) +
  coord_cartesian(x = c(0, 100), y = c(0, 100)) +
  stat_smooth() +
  labs(title="Price v mgTHC")

```


## Implement RF

```{r TFIDFfunction, include=FALSE}
#key dataframes: e %>% filter(dominant=='CBD'), edibles %>% filter(dominant=='THC', invtype=='Solid Edible')
library(tm)
library(qdap)

#Converts product name vector to docterm matrix (TF-IDF normalization)
names_DocTermMatrix <- function (productnames1) {
  productnames <- gsub("([0-9])", "\\1 ", as.character(productnames1)) #add space betw numbers
  productnames <- gsub("[][!#$%()*,.:;<=>@^_|~.{}''']", " ", productnames) #space btw punctuation
  productnames <- removeNumbers(productnames)
  productnames <- tolower(productnames)
  productnames <- replace_symbol(productnames)
  productnames <- removePunctuation(productnames)

  productnames <- removeWords(productnames, c("oz", "mg")) #remove stopwords

  productnames <- stripWhitespace(productnames) # do this last as things are deleted
  productnames <- trimws(productnames, which = c("both", "left", "right")) #trim ends

  #productnames_DTM <- DocumentTermMatrix(Corpus(VectorSource(productnames)))

  #calculate tf idf matrix
  productnames_DTM <- DocumentTermMatrix(Corpus(VectorSource(productnames)),
                                              control = list(weighting = function(x) weightTfIdf(x, normalize = FALSE)))

  productnames_DTM <- as.data.frame(as.matrix(productnames_DTM))
  return(productnames_DTM)
}
```

```{r RFfunction, include=FALSE}
# starting values for parameters

estTHC_RFcv <- function(data, n_pc, n_cv_folds, n_tree, cv = FALSE) {
  
  # Remove missingness
  data_nomissing <- data %>% 
    filter(!is.na(sale_time),
           !is.na(avgincome)) # sometimes this is missing
  
    # Declare parameters for extrapolation from sample to population
  # Find number of observations in data that are not missing (input to model)
  n_sample <- nrow(data_nomissing) 
  
  # Get population size: # rows of liquid edibles found to be THC-dominant (est'd from sample)
  # Note: we are assuming there is no CBD in the THC-dominant edibles for now.
  n_pop <- ifelse(unique(data_nomissing$inventorytype)==23, 
                  n_liquid_rows * liq_pct_THC, 
                  n_solid_rows * sol_pct_THC) 
  
  sample_pop_inflator <- n_pop / n_sample # scale sample estimate to population estimate
  
  # Make TF-IDF matrix and get PCAs
  tfidf <- names_DocTermMatrix(data_nomissing$inv_productname) # Compute PCAs
  tfidf_pca <- prcomp(tfidf) # don't scale; keep IDF weightings
  tfidf <- tfidf_pca$x[, 1:n_pc] # Select n PCs (for speed)
  
  # Add TF-IDF features to data
  data_nomissing <- data_nomissing %>% # Variables used on RHS include:
    select(
      sale_time,
      price_x,
      pricetime, # interaction b/w price * sales
      # weight, # quantity
      mgTHC, # mgTHC from label
      store_loc, # storeID
      avgincome, # avg income in store's tract
      pcttopbracket # percent of pop in top income bracket in store's tract
    ) %>%
    cbind(tfidf) # Add on TFIDF matrix
  
  # Separate to train and test
  train <- data_nomissing %>% filter(!is.na(mgTHC))
  test <- data_nomissing %>% filter(is.na(mgTHC))
  

  
  ##### Implement RF without cv
  RF <- randomForest(mgTHC ~.,
                     data = train,
                     ntree = n_tree)
  # Get predictions from RF
  test$pred <- predict(RF, test)
  test <- test %>%
    mutate(year = lubridate::year(as.POSIXct(sale_time, origin='1970-01-01')),
           month =  lubridate::month(as.POSIXct(sale_time, origin='1970-01-01')))
  train <- train %>%
    mutate(year = lubridate::year(as.POSIXct(sale_time, origin='1970-01-01')),
           month =  lubridate::month(as.POSIXct(sale_time, origin='1970-01-01')))

  ##### Implement RF with cv
  # Prep for k-fold cross-validated RF
  train$partition <- sample(1:n_cv_folds, nrow(train), replace=TRUE)
  
  results_cv <- list()
  
  if(cv) {
    # Implement k-fold Random Forests
    for (k in 1:n_cv_folds){
      
      # Separate to training/test
      traincv <- train[train$partition != k, ]
      testcv <- train[train$partition == k, ]
    
      # implement RF with k-fold cv and n_tree trees
      # train error drastically decreases by ntree 100, and more so at ntree 250
      RF <- randomForest(mgTHC ~.,
                         data = traincv %>% select(-partition, -year, -month),
                         ntree = n_tree) 
      
      # add predictions from test data
      testcv$pred <- predict(RF, testcv)
    
      # Summarize results
      results_cv$meanError[k] <- mean(abs(testcv$pred - testcv$mgTHC))
    }
  }
  
  # Final results
  output_results <- list()
  
  output_results$alltime <-
    c('samplekgTHC' = (sum(train$mgTHC, na.rm=T) + sum(test$pred, na.rm=T)) / 1e6, # estimated in sample (all THC > CBD from 100k query)
      'populationkgTHC' = (sum(train$mgTHC, na.rm=T) + sum(test$pred, na.rm=T)) * sample_pop_inflator / 1e6, # after scaling up (assumes no CBD>THC, which must be fixed)
      'cvmeanerror' = ifelse(cv, mean(results_cv$meanError), NA))
    
  # Final results by year-month
  output_results$monthly <-
    rbind(train %>% select(year, month, pred=mgTHC),
          test %>% select(year, month, pred)) %>%
      group_by(year, month) %>%
      summarise(samplekgTHC = sum(pred, na.rm=T) / 1e6,
                popkgTHC = samplekgTHC * sample_pop_inflator)
  
  output_results
}
```



### Liquid Edibles

```{r liquidRF, echo = TRUE}
liq_est <- estTHC_RFcv(data = edibles %>% filter(invtype=="Liquid Edible", dominant=="THC"),
            n_pc = 200 / divisor, # orig 294
            n_cv_folds = 5, # orig: 5
            n_tree = 200 / divisor, # orig: 200
            cv=TRUE
  )
# debug(estTHC_RFcv)
```

```{r liquidRFresults}
# RF results
liq_est$alltime %>% 
  kable(caption="RF: sample estimate; pop est; CV error")

# Annual totals
liq_est$monthly %>% 
  group_by(year) %>% 
  summarise(popkgTHC = sum(popkgTHC)) %>% 
  arrange(year) %>%
  kable(caption="THC est'd for THC-dominant Liquid Edibles by year")

# Chart year-month totals
ggplot(data=liq_est$monthly) +
  geom_col(aes(x=month, y=popkgTHC)) + facet_grid(~year) +
  labs(title='kg THC from thc-dominant liquid edibles', digits=2)

# FY total
liq_est$monthly %>% 
  ungroup() %>%
        filter((year==2016 & month >= 7) | (year ==2017 & month <= 6)) %>%
        summarise(popkgTHC = sum(popkgTHC)) %>%
  kable(caption="July 2016 - June 2017 total", digits=2)
```

### Solid Edibles

```{r solidRF, eval = T}
sol_est <- estTHC_RFcv(data = edibles %>% filter(dominant=='THC', invtype=='Solid Edible'),
            n_pc = 200 / divisor, # orig 294
            n_cv_folds = 5, # orig: 5
            n_tree = 200 / divisor, # orig: 200
            cv=TRUE
)
```

```{r solidRFresults}
# RF results
sol_est$alltime %>% 
  kable(caption="RF: sample estimate; pop est; CV error")

# Plot year-month
ggplot(sol_est$monthly) +
  geom_col(aes(x=month, y=popkgTHC)) + facet_grid(~year) +
  labs(title='kg THC from THC-dominant solid edibles', digits=2)

# Annual totals
sol_est$monthly %>% 
  group_by(year) %>% 
  summarise(popkgTHC = sum(popkgTHC)) %>% 
  arrange(year) %>%
  kable(caption="THC est'd for THC-dominant Solid Edibles by year")

# FY total
sol_est$monthly %>% 
  ungroup() %>%
        filter((year==2016 & month >= 7) | (year ==2017 & month <= 6)) %>%
        summarise(popkgTHC = sum(popkgTHC)) %>%
  kable(caption="July 2016 - June 2017 total", digits=2)

```

# Non-edibles 

```{r, eval=FALSE}
# Get potency totals from non-edibles
#query: getkgTHCCBDretail
========
SELECT month, year, invtype,
  sum(totalthc * usableweight) * 10 / 1000000 as kgTHC,
  sum(totalcbd * usableweight) * 10 / 1000000 as kgCBD
FROM(
  SELECT
    thc+0.877*thca AS totalthc,
    CASE
      WHEN cbda is null THEN cbd
      ELSE cbd+0.877*cbda END AS totalcbd,
    invtype,
    usableweight,
    month,
    year
  FROM [rand-systems:full_WA_data__proper.Retail_ALL]
  WHERE invtype not IN ("Liquid Marijuana Infused Edible", "Solid Marijuana Infused Edible"))
GROUP BY year, month, invtype
========
```

```{r}
nonedible <- read.csv("../data/kgTHCCBDretailnonedible.csv")
ggplot(nonedible,
       aes(x=month, y=kgTHC)) + geom_col() + facet_grid(~year)
```



# All

```{r, eval = T}
edibles_combined <- bind_rows(list(
  liq_est$monthly %>% select(month, year, kgTHC =popkgTHC) %>% mutate(invtype="Liquid Edibles", kgCBD= NA),
  sol_est$monthly %>% select(month, year, kgTHC =popkgTHC) %>% mutate(invtype="Solid Edibles", kgCBD= NA)))

ggplot(edibles_combined, aes(x=month, y=kgTHC, fill=invtype)) +
  geom_col() + facet_grid(~year) +
  labs(title='kgTHC sold (edibles)', y="kg THC estimated")

combined <- 
  bind_rows(
  list(
    nonedible %>% select(month, year, invtype, kgTHC, kgCBD),
    edibles_combined))

ggplot(combined, aes(x=month, y=kgTHC, fill=invtype)) +
  geom_col() + facet_grid(~year) +
  labs(title='kgTHC sold')

# Save estimates if you want to
if (export_estimates == T) write.csv(combined, export_filename)
```




```{r, eval=FALSE, include=FALSE}
B19001e2	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): Less than $10,000: Households -- (Estimate)
B19001m2	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): Less than $10,000: Households -- (Margin of Error)
B19001e3	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $10,000 to $14,999: Households -- (Estimate)
B19001m3	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $10,000 to $14,999: Households -- (Margin of Error)
B19001e4	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $15,000 to $19,999: Households -- (Estimate)
B19001m4	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $15,000 to $19,999: Households -- (Margin of Error)
B19001e5	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $20,000 to $24,999: Households -- (Estimate)
B19001m5	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $20,000 to $24,999: Households -- (Margin of Error)
B19001e6	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $25,000 to $29,999: Households -- (Estimate)
B19001m6	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $25,000 to $29,999: Households -- (Margin of Error)
B19001e7	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $30,000 to $34,999: Households -- (Estimate)
B19001m7	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $30,000 to $34,999: Households -- (Margin of Error)
B19001e8	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $35,000 to $39,999: Households -- (Estimate)
B19001m8	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $35,000 to $39,999: Households -- (Margin of Error)
B19001e9	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $40,000 to $44,999: Households -- (Estimate)
B19001m9	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $40,000 to $44,999: Households -- (Margin of Error)
B19001e10	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $45,000 to $49,999: Households -- (Estimate)
B19001m10	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $45,000 to $49,999: Households -- (Margin of Error)
B19001e11	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $50,000 to $59,999: Households -- (Estimate)
B19001m11	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $50,000 to $59,999: Households -- (Margin of Error)
B19001e12	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $60,000 to $74,999: Households -- (Estimate)
B19001m12	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $60,000 to $74,999: Households -- (Margin of Error)
B19001e13	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $75,000 to $99,999: Households -- (Estimate)
B19001m13	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $75,000 to $99,999: Households -- (Margin of Error)
B19001e14	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $100,000 to $124,999: Households -- (Estimate)
B19001m14	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $100,000 to $124,999: Households -- (Margin of Error)
B19001e15	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $125,000 to $149,999: Households -- (Estimate)
B19001m15	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $125,000 to $149,999: Households -- (Margin of Error)
B19001e16	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $150,000 to $199,999: Households -- (Estimate)
B19001m16	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $150,000 to $199,999: Households -- (Margin of Error)
B19001e17	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $200,000 or more: Households -- (Estimate)
B19001m17	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $200,000 or more: Households -- (Margin of Error)
```



# Appendix

## Detailed Results

### Edible THC monthly

```{r}
kable(liq_est$monthly %>% arrange(year, month))
kable(sol_est$monthly %>% arrange(year, month))
```

## Query for MJ edible export
```{r, eval=FALSE}
SELECT
  CASE
    WHEN thca is null THEN thc
    ELSE thc + (0.877 * thca) END AS Potency_THC,
  CASE
    WHEN cbda is null THEN cbd
    ELSE cbd + (0.877 * cbda) END AS Potency_CBD,
  inv_productname, transactionid,
  sale_time, weight,
  #usableweight #note: no useable weights here
  inventorytype, #22 = solid; 23 = liquid,
  price_x,
  #gram_price_x, #no usable weights here,
  #invtype #note: abbreviated in inventorytype
  store_loc
  
  FROM(
    SELECT store_loc,  thc, thca, cbd, cbda,
    inv_productname, transactionid, #maybe useful for basket analysis?
    sale_time, weight, usableweight, inventorytype, price_x, gram_price_x,
    invtype

    FROM [rand-systems:full_WA_data__proper.Retail_ALL]
    
    WHERE 
      invtype IN ('Solid Marijuana Infused Edible', 'Liquid Marijuana Infused Edible')
      AND RAND() < 220000/4972181
      
    LIMIT 200000
    )
```

