---
title: "Estimate mgTHC (Edible and non-Edible)"
author: "Steven Davenport"
date: "`r format(Sys.time(), '%d %B, %Y %H:%M(%S)')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
---

This comes from a document originally written by Anhvinh Doanvo. It will impute edible potency in the style used by the CMU team.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, messages=FALSE, warnings = FALSE)
options(scipen = 7)
library(plyr); library(tidyverse)
library(knitr); library(glmnet); library(randomForest); library(tm)
library(qdap); library(ranger)
source("CMU_code_share_av.R") #Import "search_productname(arg)", where arg = inventory product name

# load edibles data
# "../data/ediblesFY1617sample100k.csv"
edibles <- read.csv("../data/ediblesAlltimeSample200k.csv") 

# Data on size of table in BigQuery (for scaling to population)
# FOR 2017 DATA
n_edible_rows <- 4972181 # total number of rows in edible table from BigQuery for 2017
n_solid_rows <- 4004175 # 22
n_liquid_rows <- 968006 # 23

# FOR FY 2017 (july 1 2016 - june 30 2017)
#???
#???
#???

# all-time
n_solid_rows <- 8487415 # 22
n_liquid_rows <- 2150470 # 23
n_edible_rows <-  n_solid_rows + n_liquid_rows
```

# Parameters

```{r parameters, echo = TRUE}
divisor <- 10 # scaleability parameter
n_sample_obs <- nrow(edibles) / divisor # number of obs to sample from all edibles from SQL export
```

# Census Data

```{r calculate income index, echo = F}
censusdata <- read.csv("../data/biotrackthc_locations_cenus_joined.csv") # Steve's directory

# This calculates average income by census tract
censusdata$avgincome <- (censusdata$X19_INCOME_B19001e2 * 5000 +
censusdata$X19_INCOME_B19001e3 * 12500 +
censusdata$X19_INCOME_B19001e4 * 17500 +
censusdata$X19_INCOME_B19001e5 * 22500 +
censusdata$X19_INCOME_B19001e6 * 27500 +
censusdata$X19_INCOME_B19001e7 * 32500 +
censusdata$X19_INCOME_B19001e8 * 37500 +
censusdata$X19_INCOME_B19001e9 * 42500 +
censusdata$X19_INCOME_B19001e10 * 47500 +
censusdata$X19_INCOME_B19001e11 * 55000 +
censusdata$X19_INCOME_B19001e12 * 67500 +
censusdata$X19_INCOME_B19001e13 * 87500 +
censusdata$X19_INCOME_B19001e14 * 112500 +
censusdata$X19_INCOME_B19001e15 * 137500 +
censusdata$X19_INCOME_B19001e16 * 175000) / (censusdata$X19_INCOME_B19001e2 +
censusdata$X19_INCOME_B19001e3 +
censusdata$X19_INCOME_B19001e4 +
censusdata$X19_INCOME_B19001e5 +
censusdata$X19_INCOME_B19001e6 +
censusdata$X19_INCOME_B19001e7 +
censusdata$X19_INCOME_B19001e8 +
censusdata$X19_INCOME_B19001e9 +
censusdata$X19_INCOME_B19001e10 +
censusdata$X19_INCOME_B19001e11 +
censusdata$X19_INCOME_B19001e12 +
censusdata$X19_INCOME_B19001e13 +
censusdata$X19_INCOME_B19001e14 +
censusdata$X19_INCOME_B19001e15 +
censusdata$X19_INCOME_B19001e16) #for lower incomes, get average estimated

# This gets percent of population in top bracket
censusdata$pcttopbracket <- censusdata$X19_INCOME_B19001e17 / (censusdata$X19_INCOME_B19001e2 +
censusdata$X19_INCOME_B19001e3 +
censusdata$X19_INCOME_B19001e4 +
censusdata$X19_INCOME_B19001e5 +
censusdata$X19_INCOME_B19001e6 +
censusdata$X19_INCOME_B19001e7 +
censusdata$X19_INCOME_B19001e8 +
censusdata$X19_INCOME_B19001e9 +
censusdata$X19_INCOME_B19001e10 +
censusdata$X19_INCOME_B19001e11 +
censusdata$X19_INCOME_B19001e12 +
censusdata$X19_INCOME_B19001e13 +
censusdata$X19_INCOME_B19001e14 +
censusdata$X19_INCOME_B19001e15 +
censusdata$X19_INCOME_B19001e16 +
censusdata$X19_INCOME_B19001e17) # for very high-income indivduals, just grab percentage in that bracket

store_incomes <- data.frame(store_loc = censusdata$ID,
                           avgincome = censusdata$avgincome,
                           pcttopbracket = censusdata$pcttopbracket)

# de-duplicate; take average for stores w multiple locations
store_incomes <- store_incomes[!duplicated(store_incomes),]
store_avg_income <- aggregate(avgincome ~ store_loc, 
                          data = store_incomes,
                          FUN = mean)
store_top_pct <- aggregate(pcttopbracket ~ store_loc, 
                          data = store_incomes,
                          FUN = mean)


store_incomes <- merge(x = store_avg_income, y = store_top_pct, by = "store_loc")  # NOT inv_location
rm(store_avg_income)
rm(store_top_pct)
##NEED TO CHECK THIS WORK

```

Census data was downloaded from [this source](https://www.census.gov/geo/maps-data/data/tiger-data.html). I selected the 2015 "detailed tables" for the Washington State block group. The "X19_INCOME" table was table-joined to the "ACS_2015_5YR_BG_53_WASHINGTON" shapefile using X19's GEOID and ACS's GEOID_Data fields. Furthermore, the stores identified in the biotrackthc_locations table were geocoded using their latitude and longitudinal coordinates.

These stores were spatial-joined to their associated census tract to relate them to demographic data of their surrounding region. Using this data, an 'income index' was calculated for each store by compositing counts of individuals in each income bracket per store in each census tract. The data coding information sourced from the American Community Survey is in a code chunk in this rmd file.

# Edibles

## Prep Data

```{r prep edibles data}
# Load random sample of edible observations
edibles <- edibles %>%
  
  # Sample for computational speed
  dplyr::sample_n(n_sample_obs) %>%
  
  # Parse saletime and interaction term for price * saletime
  mutate(sale_time = as.numeric(as.POSIXct(as.character(sale_time))), 
         pricetime = (sale_time - mean(sale_time)) * price_x) %>% # TODO: isn't this unnecessary in an RF?
  
  
  # Remove rows with blank THC/date/inventorytype
  filter(!is.na(Potency_THC),
         !is.na(sale_time),
         !is.na(inventorytype))

# merge on census data (store income)
edibles <- edibles %>%
  left_join(store_incomes)

# Topcode THC values
# This does not affect anything as you shouldn't be using this column. TODO: delete?
edibles$Potency_THC <- ifelse(edibles$Potency_THC > 100, 100, edibles$Potency_THC)

# get MG THC from label where available 
edibles <- edibles %>%
  # Add mgTHC estimates
  mutate(mgTHC = weight * 
           search_productname(edibles$inv_productname)$mg_text_max %>% 
           # topcode @ 500mg THC (medical market maximum)
           ifelse(. > 500, 500, .)) 

# partition to THC- and CBD-dominant edibles
# TODO: REMOVE AS THE CBD is not being correctly estimated??
edibles_CBD <- edibles %>% filter(Potency_CBD > Potency_THC)
edibles <- edibles %>% filter(Potency_CBD <= Potency_THC)

# Partition to liquid and solid edibles
edibles_liq <- edibles %>% filter(inventorytype == 23)
edibles_sol <- edibles %>% filter(inventorytype == 22)

# TODO: fix scale variable to adjust for portion of non-THC dominant edibles
```

## Visualize mgTHC and Price

```{r plot}
# big picture including 500
# ggplot(edibles, aes(x = mgTHC)) +
#   geom_histogram() +
#   facet_grid(.~ inventorytype)

ggplot(edibles, aes(x = mgTHC)) +
  geom_histogram() +
  facet_grid(.~ inventorytype) + xlim(c(0, 100)) +
  labs(title="Distribution mgTHC")

ggplot(edibles, aes(y = price_x, x = mgTHC)) +
  geom_point(alpha = 0.1) +
  facet_grid(.~ inventorytype) +
  coord_cartesian(x = c(0, 100), y = c(0, 100)) +
  stat_smooth() +
  labs(title="Price v mgTHC")
```

## Implement RF

```{r TFIDFfunction, include=FALSE}
#key dataframes: edibles_liq, edibles_sol
library(tm)
library(qdap)

#Converts product name vector to docterm matrix (TF-IDF normalization)
names_DocTermMatrix <- function (productnames1) {
  productnames <- gsub("([0-9])", "\\1 ", as.character(productnames1)) #add space betw numbers
  productnames <- gsub("[][!#$%()*,.:;<=>@^_|~.{}''']", " ", productnames) #space btw punctuation
  productnames <- removeNumbers(productnames)
  productnames <- tolower(productnames)
  productnames <- replace_symbol(productnames)
  productnames <- removePunctuation(productnames)

  productnames <- removeWords(productnames, c("oz", "mg")) #remove stopwords

  productnames <- stripWhitespace(productnames) # do this last as things are deleted
  productnames <- trimws(productnames, which = c("both", "left", "right")) #trim ends

  #productnames_DTM <- DocumentTermMatrix(Corpus(VectorSource(productnames)))

  #calculate tf idf matrix
  productnames_DTM <- DocumentTermMatrix(Corpus(VectorSource(productnames)),
                                              control = list(weighting = function(x) weightTfIdf(x, normalize = FALSE)))

  productnames_DTM <- as.data.frame(as.matrix(productnames_DTM))
  return(productnames_DTM)
}
```

```{r RFfunction, include=FALSE}
# starting values for parameters

estTHC_RFcv <- function(data, n_pc, n_cv_folds, n_tree, cv = FALSE) {
  
  # Declare parameters for extrapolation from sample to population
  n_sample <- nrow(data) # Find number of observations in data
  n_pop <- ifelse(unique(data$inventorytype)==23, n_liquid_rows, n_solid_rows) # Liquid (23) is smaller, solid(22) is bigger
  
  # Make TF-IDF matrix and get PCAs
  tfidf <- names_DocTermMatrix(data$inv_productname) # Compute PCAs
  tfidf_pca <- prcomp(tfidf) # don't scale; keep IDF weightings
  tfidf <- tfidf_pca$x[, 1:n_pc] # Select n PCs (for speed)
  
  # Add TF-IDF features to data
  data <- data %>% # Variables used on RHS include:
    select(
      sale_time,
      price_x,
      pricetime, # interaction b/w price * sales
      # weight, # quantity
      mgTHC, # mgTHC from label
      store_loc, # storeID
      avgincome, # avg income in store's tract
      pcttopbracket # percent of pop in top income bracket in store's tract
    ) %>%
    cbind(tfidf) # Add on TFIDF matrix
  
  # Separate to train and test
  train <- data %>% filter(!is.na(mgTHC))
  test <- data %>% filter(is.na(mgTHC))
  
  ##### Implement RF without cv
  RF <- randomForest(mgTHC ~.,
                     data = train,
                     ntree = n_tree)
  # Get predictions from RF
  test$pred <- predict(RF, test)
  test <- test %>%
    mutate(year = lubridate::year(as.POSIXct(sale_time, origin='1970-01-01')),
           month =  lubridate::month(as.POSIXct(sale_time, origin='1970-01-01')))

  ##### Implement RF with cv
  # Prep for k-fold cross-validated RF
  train$partition <- sample(1:n_cv_folds, nrow(train), replace=TRUE)
  
  results_cv <- list()
  
  if(cv) {
    # Implement k-fold Random Forests
    for (k in 1:n_cv_folds){
      
      # Separate to training/test
      traincv <- train[train$partition != k, ]
      testcv <- train[train$partition == k, ]
    
      # implement RF with k-fold cv and n_tree trees
      # train error drastically decreases by ntree 100, and more so at ntree 250
      RF <- randomForest(mgTHC ~.,
                         data = traincv %>% select(-partition),
                         ntree = n_tree) 
      
      # add predictions from test data
      testcv$pred <- predict(RF, testcv)
    
      # Summarize results
      results_cv$meanError[k] <- mean(abs(testcv$pred - testcv$mgTHC))
    }
  }
  
  # Final results
  output_results <- list()
  
  output_results$alltime <-
    c('samplekgTHC' = sum(test$pred) / 1e6, # estimated in sample (all THC > CBD from 100k query)
      'populationkgTHC' = sum(test$pred) * n_pop / n_sample / 1e6, # after scaling up (assumes no CBD>THC, which must be fixed)
      'cvmeanerror' = ifelse(cv, mean(results_cv$meanError), NA))
    
  # Final results by year-month
  output_results$monthly <-
    test %>%
      group_by(year, month) %>%
      summarise(samplekgTHC = sum(pred) / 1e6,
                popkgTHC = samplekgTHC * n_pop / n_sample)
  
  output_results
}
```

```{r liquidRF, echo = TRUE}
cat("Liquid Edibles")
# undebug(estTHC_RFcv)
# debug(estTHC_RFcv)
# divisor <- 10

liq_est <- estTHC_RFcv(data = edibles_liq,
            n_pc = 200 / divisor, # orig 294
            n_cv_folds = 5, # orig: 5
            n_tree = 200 / divisor, # orig: 200
            cv=TRUE
  )

ggplot(data=liq_est$monthly) +
  geom_col(aes(x=month, y=popkgTHC)) + facet_wrap(~year) +
  labs(title='kg THC from liquid edibles')

liq_est$alltime
```

```{r solidRF}
cat("solid Edibles")
sol_est <- estTHC_RFcv(data = edibles_sol,
            n_pc = 300 , # orig 294
            n_cv_folds = 5, # orig: 5
            n_tree = 200, # orig: 200
            cv=TRUE
)

sol_est$alltime

ggplot(sol_est$monthly) +
  geom_col(aes(x=month, y=popkgTHC)) + facet_wrap(~year) +
  labs(title='kg THC from solid edibles')
```

# Non-edibles 

```{r, eval=FALSE}
# Get potency totals from non-edibles
#query: getkgTHCCBDretail
========
SELECT month, year, invtype,
  sum(totalthc * usableweight) * 10 / 1000000 as kgTHC,
  sum(totalcbd * usableweight) * 10 / 1000000 as kgCBD
FROM(
  SELECT
    thc+0.877*thca AS totalthc,
    CASE
      WHEN cbda is null THEN cbd
      ELSE cbd+0.877*cbda END AS totalcbd,
    invtype,
    usableweight,
    month,
    year
  FROM [rand-systems:full_WA_data__proper.Retail_ALL]
  WHERE invtype not IN ("Liquid Marijuana Infused Edible", "Solid Marijuana Infused Edible"))
GROUP BY year, month, invtype
========
```

```{r}
nonedible <- read.csv("../data/kgTHCCBDretailnonedible.csv")
ggplot(nonedible,
       aes(x=month, y=kgTHC)) + geom_col() + facet_wrap(~year)

```

```{r}
edibles_combined <- bind_rows(list(
  liq_est$monthly %>% select(month, year, kgTHC =popkgTHC) %>% mutate(invtype="Liquid Edibles", kgCBD= NA),
  sol_est$monthly %>% select(month, year, kgTHC =popkgTHC) %>% mutate(invtype="Solid Edibles", kgCBD= NA)))

ggplot(edibles_combined, aes(x=month, y=kgTHC, fill=invtype)) +
  geom_col() + facet_grid(~year) +
  labs(title='kgTHC sold (edibles)')

combined <- 
  bind_rows(
  list(
    nonedible %>% select(month, year, invtype, kgTHC, kgCBD),
    edibles_combined))

ggplot(combined, aes(x=month, y=kgTHC, fill=invtype)) +
  geom_col() + facet_grid(~year) +
  labs(title='kgTHC sold')

    
```



```{r, eval=FALSE, include=FALSE}
B19001e2	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): Less than $10,000: Households -- (Estimate)
B19001m2	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): Less than $10,000: Households -- (Margin of Error)
B19001e3	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $10,000 to $14,999: Households -- (Estimate)
B19001m3	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $10,000 to $14,999: Households -- (Margin of Error)
B19001e4	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $15,000 to $19,999: Households -- (Estimate)
B19001m4	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $15,000 to $19,999: Households -- (Margin of Error)
B19001e5	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $20,000 to $24,999: Households -- (Estimate)
B19001m5	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $20,000 to $24,999: Households -- (Margin of Error)
B19001e6	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $25,000 to $29,999: Households -- (Estimate)
B19001m6	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $25,000 to $29,999: Households -- (Margin of Error)
B19001e7	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $30,000 to $34,999: Households -- (Estimate)
B19001m7	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $30,000 to $34,999: Households -- (Margin of Error)
B19001e8	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $35,000 to $39,999: Households -- (Estimate)
B19001m8	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $35,000 to $39,999: Households -- (Margin of Error)
B19001e9	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $40,000 to $44,999: Households -- (Estimate)
B19001m9	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $40,000 to $44,999: Households -- (Margin of Error)
B19001e10	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $45,000 to $49,999: Households -- (Estimate)
B19001m10	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $45,000 to $49,999: Households -- (Margin of Error)
B19001e11	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $50,000 to $59,999: Households -- (Estimate)
B19001m11	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $50,000 to $59,999: Households -- (Margin of Error)
B19001e12	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $60,000 to $74,999: Households -- (Estimate)
B19001m12	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $60,000 to $74,999: Households -- (Margin of Error)
B19001e13	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $75,000 to $99,999: Households -- (Estimate)
B19001m13	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $75,000 to $99,999: Households -- (Margin of Error)
B19001e14	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $100,000 to $124,999: Households -- (Estimate)
B19001m14	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $100,000 to $124,999: Households -- (Margin of Error)
B19001e15	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $125,000 to $149,999: Households -- (Estimate)
B19001m15	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $125,000 to $149,999: Households -- (Margin of Error)
B19001e16	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $150,000 to $199,999: Households -- (Estimate)
B19001m16	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $150,000 to $199,999: Households -- (Margin of Error)
B19001e17	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $200,000 or more: Households -- (Estimate)
B19001m17	HOUSEHOLD INCOME IN THE PAST 12 MONTHS (IN 2015 INFLATION-ADJUSTED DOLLARS): $200,000 or more: Households -- (Margin of Error)
```



# Appendix

## Query for MJ edible export
```{r, eval=FALSE}
# TABLE: Edibles2017; query: imputedEdibles2017
SELECT store_loc,  thc, thca, cbd, cbda,
  inv_productname, transactionid, #maybe useful for basket analysis?
  sale_time, weight, usableweight, inventorytype, price_x, gram_price_x,
  invtype

FROM [rand-systems:full_WA_data__proper.Retail_ALL]
WHERE invtype IN ('Solid Marijuana Infused Edible', 'Liquid Marijuana Infused Edible')
AND sale_time > cast('2017-01-01 00:00:00.00 UTC' as timestamp)
==========================================

# SECOND QUERY: TABLE: Edibles2017pt2; query: imputeEdibles2017pt2
SELECT (thc + (0.877 * thca)) AS Potency_THC,
  (cbd + (cbda *  (0.877)) AS Potency_CBD,
  inv_productname, transactionid,
  sale_time, weight,
  #usableweight #note: no useable weights here
  inventorytype, #22 = solid; 23 = liquid,
  price_x,
  #gram_price_x, #no usable weights here,
  #invtype #note: abbreviated in inventorytype
  store_loc

FROM [rand-systems:full_WA_data__proper.edibles2017]

# THIRD QUERY: get random sample
=======Random Sampling
SELECT *
FROM [rand-systems:full_WA_data__proper.edibles2017step2]
WHERE RAND() < 100000/4972181  #format: rough number of rows desired / total rows in table

#this gets approximate random sample with scalable code
```



<!-- # Edible CBD Products -->

<!-- **TO DO: This is a little more complicated here. Need to estimate usable weight, NOT CBD/THC content directly. THEN use this to get THC content.** -->

<!-- ## Liquids -->

<!-- ```{r} -->
<!-- edibles_cbd_liq <- edibles_CBD[edibles_CBD$inventorytype == 23,] -->

<!-- #train model -->
<!-- edibles_cbd_liq_train <- edibles_cbd_liq  %>% filter(!is.na(mgTHC)) -->
<!-- edibles_cbd_liq.lm <- lm(mgTHC ~ price_x + pricetime, edibles_cbd_liq_train) -->
<!-- #estimate -->
<!-- edibles_cbd_liq_impute <- edibles_cbd_liq  %>% filter(1is.na(mgTHC)) -->
<!-- edibles_cbd_liq_impute$mgTHC <- predict(edibles_cbd_liq.lm, edibles_cbd_liq_impute) -->

<!-- summary(edibles_cbd_liq.lm) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- edibles_cbd_liq_summary <- data.frame(type = as.character(), mgCBD = as.numeric(), sd = as.numeric()) -->

<!-- edibles_cbd_liq_summary <- rbind(edibles_cbd_liq_summary, -->
<!--                              data.frame(type = "Training", mgCBD = sum(edibles_cbd_liq_train$mgTHC), sd = sd(edibles_cbd_liq_train$mgTHC) / (nrow(edibles_cbd_liq_train) ^ 0.5))) -->

<!-- edibles_cbd_liq_summary <- rbind(edibles_cbd_liq_summary, -->
<!--                              data.frame(type = "Imputed", mgCBD = sum(edibles_cbd_liq_impute$mgTHC), sd = sd(edibles_cbd_liq_impute$mgTHC) / (nrow(edibles_cbd_liq_impute) ^ 0.5))) -->

<!-- kable(cbind(edibles_cbd_liq_summary[,1], (edibles_cbd_liq_summary[,2:3])* n_edible_rows / 100000)) -->
<!-- ``` -->

<!-- ## Solids -->

<!-- ```{r} -->
<!-- edibles_cbd_sol <- edibles_CBD[edibles_CBD$inventorytype == 22,] -->

<!-- #train model -->
<!-- edibles_cbd_sol_train <- edibles_cbd_sol  %>% filter(!is.na(mgTHC)) -->
<!-- edibles_cbd_sol.lm <- lm(mgTHC ~ price_x + pricetime, edibles_cbd_sol_train) -->
<!-- #estimate -->
<!-- edibles_cbd_sol_impute <- edibles_cbd_sol %>% filter(!is.na(mgTHC)) -->
<!-- edibles_cbd_sol_impute$mgTHC <- predict(edibles_cbd_sol.lm, edibles_cbd_sol_impute) -->


<!-- summary(edibles_cbd_sol.lm ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- edibles_cbd_sol_summary <- data.frame(type = as.character(), mgCBD = as.numeric(), sd = as.numeric()) -->

<!-- edibles_cbd_sol_summary <- rbind(edibles_cbd_sol_summary, -->
<!--                              data.frame(type = "Training", mgCBD = sum(edibles_cbd_sol_train$mgTHC), sd = sd(edibles_cbd_sol_train$mgTHC) / (nrow(edibles_cbd_sol_train) ^ 0.5))) -->

<!-- edibles_cbd_sol_summary <- rbind(edibles_cbd_sol_summary, -->
<!--                              data.frame(type = "Imputed", mgCBD = sum(edibles_cbd_sol_impute$mgTHC), sd = sd(edibles_cbd_sol_impute$mgTHC) / (nrow(edibles_cbd_sol_impute) ^ 0.5))) -->

<!-- kable(cbind(edibles_cbd_sol_summary[,1], (edibles_cbd_sol_summary[,2:3])* n_edible_rows / 100000)) -->

<!-- ``` -->