---
title: "Traceability-Based Findings - Sept Draft"
author: "Steven Davenport"
date: "`r format(Sys.time(), '%B %d, %Y (%H:%M)')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

**Version history**
v1.5 - September Draft.  
v1.4 (July 3) Restructured outline; sent to JPC/BK for review.
v1.3 (June 30) restructured outline.  
v1.2 (June 30) added analysis of inventoryconversions table.  
v1.1 (June 29) clarified outline; incorporated comments from Kee Won RE methods. Was sent briefly to JPC.  
v1.0 (June 27) provided outline; finished first draft of retail tables.

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      # Graphic output
                      fig.width = 8, fig.align='center')
library(tidyverse)
library(knitr)
source("functions.r")
options(scipen=12)


# Get inventory conversions (dated)
# -- QUERY
# Run in legacy SQL
# convDetailedT
# SELECT inventorytype, inventorytype_parent, location,
#     count(*) as nConversions,
#     sum(CAST(parent_difference as float)) as parentwt,
#     sum(CAST(childweight as float)) as childwt,
#     sum(CAST(child_usableweight as float)) as childusablewt
# 
# FROM [rand-systems:full_WA_data__proper.biotrackthc_inventoryconversions_dated] 
# GROUP BY inventorytype, inventorytype_parent, location, year, month
convDetailedT <- read_csv("../gqoutput/convDetailedT.csv") %>%
  mutate(parent = getInvtype(inventorytype_parent),
         child = getInvtype(inventorytype))  %>%
  select(-inventorytype_parent, -inventorytype) %>%
  arrange(-nConversions) # TODO: Add licensee name, date?

# Make a non-timed version
convDetailed <- convDetailedT %>%
  group_by(location, parent, child) %>%
  summarise(nConversions = sum(nConversions),
            parentwt = sum(parentwt),
            childwt = sum(childwt),
            childusablewt = sum(childusablewt))
write.csv(convDetailed, "../output/conversionsDetailed.csv")

# Get Potency
# Load potency test data scores
potency <- read_csv("../data/potencytests.csv")
# clean for consistent Total THC/CBD.
potencyAnnual <-
  potency %>%
  mutate(TotalTHC = THC + 0.877 * THCA,
         TotalCBD = CBD + 0.877 * CBDA
         ) %>%
  select(TotalTHC, TotalCBD, inventorytype, invtype, test_year) %>%
  group_by(invtype, test_year) %>%
  summarise(TotalTHC = mean(TotalTHC, na.rm=T),
            TotalCBD = mean(TotalCBD, na.rm=T))
# Export file for use in estimating THC content of products!
potencyAnnual %>%
  write_csv("../data/thccbdannual.csv")


# Get data on conversion paths (e.g. for prevalence)
convPaths <- read_csv("../gqoutput/results-20180630-124915.csv") %>%
  mutate(parent = getInvtype(inventorytype_parent),
         child = getInvtype(inventorytype))  %>%
  select(parent, child, nConversions) %>%
  arrange(-nConversions)

# -- Inventory Conversion parent-child
# SELECT inventorytype, inventorytype_parent, count(*) as nConversions
# FROM [full_WA_data.biotrackthc_inventoryconversions]
# GROUP BY inventorytype, inventorytype_parent


# Get spending per year by inventory tpe
# GoogleQuery: RetailUSDxType
# SELECT invtype,
#   YEAR(sale_time) as YEAR,
#   MONTH(sale_time) as MONTH,
#   -- number of rows (item-transactions)
#   count(*) as itemtransactions,
#   sum(price_x) as price_x,
#   -- TODO: After remaking retail view, replace with proper "TotalTHC"
#   -- TODO: Replace with weighted average, w wts varied by inventorytype
#   avg(thc + thca*0.877) as totalTHC,
#   -- TODO: Replace this with a cleaned version of totalCBD? (
#   avg(case when cbda is null then cbd
#        when cbda is not null then cbd + cbda * 0.877
#        end) as totalCBD,
#         --avg(cbd + (if is not null cbda, cbda *0.877, 0)) as totalCBD
#    sum(case when usableweight is not null then usableweight
#              else 0 end) as usableweight
# FROM [full_WA_data__proper.Retail_ALL]
# GROUP BY invtype, YEAR, MONTH
# ORDER BY invtype, YEAR,MONTH
retailUSDxType <- read_csv("../gqoutput/retailusd.csv") %>%
  mutate(date=make_date(YEAR, MONTH)) %>%
  # Convert to $1000s
  mutate(price_x = price_x / 1e3) %>%
  filter(
    # remove NA
    !is.na(invtype),
    # remove non-retail products in here for no reason
    !invtype%in%c("Clone", "Mature Plant"),
    # Remove the partial month of October 2017
    date <= "2017-10-01")


# Load conversion-parent table
# -- QUERY
# SELECT inventorytype_parent,
#   count(*) as nConversions,
#   sum(CAST(parent_difference as integer)) as parentwt
# FROM [full_WA_data.biotrackthc_inventoryconversions]
# GROUP BY inventorytype_parent
convParent <- read_csv("../gqoutput/results-20180630-130516.csv") %>%
  mutate(inventorytype_parent = getInvtype(inventorytype_parent)) %>%
  mutate(wtPerConv = parentwt/nConversions) %>%
  arrange(-parentwt)

# Get Transfer Volumes
# Get Ingredient weights.
# -- Query usable weight of eligible transfers
# SELECT inventorytype,
#    sum(CAST(USABLEWEIGHT as float)) * SUM(CAST(weight as float)) as usableweight,
#    sum(CAST(USABLEWEIGHT as float)) as usableweightraw
# FROM [full_WA_data.biotrackthc_inventorytransfers]
# WHERE USABLEWEIGHT is not null and CAST(inventorytype as integer) <=40
# GROUP BY inventorytype
# ORDER BY inventorytype
# transferUsableWeight <- read_csv("../gqoutput/results-20180914-110802.csv") # uw = uw * w
transferUsableWeight <- read_csv("../gqoutput/results-20180912-182538.csv") # Version w simple sum usableweight


# -- Query Sale Price of All Transfers
# SELECT inventorytype,
#    count(*) as nTransfers,
#    sum(CAST(saleprice as integer)) as saleprice
# FROM [full_WA_data.biotrackthc_inventorytransfers]
# WHERE saleprice is not null and CAST(inventorytype as integer) <=40
# GROUP BY inventorytype
# ORDER BY inventorytype
transferVolumes <- read_csv("../gqoutput/results-20180912-181851.csv")

transfers <- left_join(transferVolumes, transferUsableWeight) %>%
  mutate(invtype = getInvtype(inventorytype)) %>%
  select(invtype, nTransfers, saleprice, usableweight) %>%
  mutate(pricePer = saleprice / nTransfers) 

# Inventory Transfers
# Import inventorytransfers with 10 time points cut by ID
# -- getinventorytransfersYrMo -- ordered version
# SELECT sum(weight) as units,
#        sum(usableweight)/1000 as kg,
#        sum(saleprice)/1000 as kUSD,
#        FLOOR(rowN / 255250) as t,
#        inventorytype
#        from(
#        -- Inner Query adds row numbers by ID, cleans columns for summing
#           SELECT CAST(inventorytype as integer) as inventorytype,
#                 ROW_NUMBER() OVER(ORDER BY ID ASC) rowN,
#                 Description, location, inventoryid,
#                 case when weight is null then 0 else cast(weight as float) end as weight,
#                 case when usableweight is null then 0 else cast(usableweight as float) end as usableweight,
#                 case when saleprice is null then 0 else cast(saleprice as float) end as saleprice
#           FROM [full_WA_data__proper.biotrackthc_inventorytransfers_ordered])
# where inventorytype <= 40
# GROUP BY t, inventorytype
# order by t
# this is ordered correctly now
transfersYrMo <- read.csv("../gqoutput/invTransfersYearMonth.csv") %>% 
  mutate(inventorytype = getInvtype(inventorytype),
         pricePerG = kUSD/kg,
         unitsK=units/1e3,
         perPerUnit = kUSD/unitsK)

transfersYr <- transfersYrMo %>%
  group_by(year, inventorytype) %>%
  summarise(units = sum(units),
            kg = sum(kg),
            kUSD = sum(kUSD)) %>%
  mutate(pricePerG = kUSD/kg,
         unitsK=units/1e3,
         perPerUnit = kUSD/unitsK)
```

```{r queryconvchildWt}
# Get Ingredient weights.
# -- Outer query calculates grouped sums
# SELECT year, month, location, inventorytype, 
#     sum(childwt) as childwt, 
#     sum(childusablewt) as childusablewt,
#     count(*) as nConversions
#     -- Middle query topcodes usableweight based on invtype-specific uw:w ratio
#     FROM( SELECT year, month, location, childwt, inventorytype,
#             case when ratio_dirty > (28.5) AND inventorytype=="28" then childwt * (28.5) -- usable MJ, enforce 1 ounce
#                  when ratio_dirty > (28.5)*16*10 AND inventorytype=="30" then childwt * (28.5)*16*10  -- MJ mix: 10 pounds
#                  when ratio_dirty > (28.5)*16*2 AND inventorytype IN("5", "16") then childwt * (28.5)*16*2  --  Hash/Kief: 2 pounds
#                  when ratio_dirty > (28.5)*16*4 AND inventorytype=="18" then childwt * (28.5)*16*4  --  Co2Hashoil: 4 pounds
#                  ELSE childusablewt_dirty END AS childusablewt
#           -- Inner query fixes types and top-codes weight.
#           from( SELECT 
#                   -- top code childwt at 5000 in general (spike for mjmix; biggest value in data for OPM; maybe lower for others)
#                   -- Note: this is not sufficient to clean the MJ Mix spikes
#                   case when CAST(childweight as float) > 7000 then 7000 ELSE CAST(childweight as float) END AS childwt,
#                   CAST(child_usableweight as float) as childusablewt_dirty,
#                   CAST(child_usableweight as float) / CAST(childweight as float) AS ratio_dirty,
#                   *
#                 FROM [rand-systems:full_WA_data__proper.biotrackthc_inventoryconversions_dated]
#                 /* below to lines are useful for debugging 
#                 WHERE year == 2017 AND month IN (1,2) and cast(location as integer) == 1273
#                 order by ratio_dirty desc 
#                 */
#           )
#       )
# group by year, month, location, inventorytype

convChildT <- read.csv("../gqoutput/convChildTclean.csv") %>%
  mutate(inventorytype = getInvtype(inventorytype),
         uwper = childusablewt / childwt) # for validatinf
  

# get non-dated version
convChild <- convChildT %>%
  group_by(inventorytype) %>%
  summarise(nConversions = sum(nConversions),
            childwt = sum(childwt),
            childusablewt = sum(childusablewt),
            wtPer = childwt/nConversions,
            usablewtPer = childusablewt/nConversions
            ) %>%  arrange(-childwt)
```

## Results (Section 4)

### 4A Harvest Analysis

For this section, I will paste in data from Kee Won's analysis. Unfortunately that is not present in this DOCX but can be seen in the accompanying document.

+ Plants, Harvest Weight, Harvest per plant. See .docx

#### Waste?

We have not produced estimates for "waste" during harvest. That is possible but not yet done. We do not currently know a place in the database that tracks "waste" at other parts of the supply chain.

### 4B Amount Produced (Units, MT)

Querying the "inventory conversions" table yields data on volume of production.  The inventory conversions table records all conversions from one inventory type to another. T




This table does not contain a "date" field, so we cannot easily group events by year. However, we can still produce time-series analyses by grouping the data by the order of rows in the database. Below we produce time-series analysis in this way, sometimes cutting data into 3 time chunks (very roughly 2015, 2016, 2017). For charts, we cut the data into more time chunks to reveal trends. Data span nearly the entire supply chain:

+ Lotting stage (flower -> flower lot)
+ processing/manufacturing stage 1 (flower/OPM to intermediate extracts)
+ processing/manufacturing stage 1 (intermediate extracts to retail product)


#### "Ingredients"

```{r}
# Look only at Ingredient Types
ingrdnts <- c("Hydrocarbon Wax", "Bubble Hash", "C02 Hash Oil", "Marijuana Mix", "Food Grade Solvent Extract", 
              "Infused Dairy Butter or Fat in Solid Form", "Infused Cooking Oil",
              "Hash", "Kief")
```

Ingredient products include: `r paste0(ingrdnts, collapse="; ")`.

TODO: 

```{r}
# summary table: show kg produced by year-quarter
convChildT %>%
  filter(inventorytype%in%ingrdnts) %>%
  mutate(q = cut(month, c(0, 3.1, 6.1, 9.1, 12.1), labels=1:4),
         h = cut(month, c(0, 6.1, 12.1), labels=1:2),
         yearq = paste0(year,"-", q),
         yearh = paste0(year,"-", h)) %>%
  group_by(inventorytype, yearh) %>%
  summarise(KG = sum(childwt)/1e3) %>%
  spread(yearh, KG) %>%
  arrange(-`2017-1`) %>%
  filter(!is.na(`2016-2`)) %>%
  kable(digits=1, caption="Ingredient Production (KG) by 6-month period")

```

#### Retail Flower

```{r}
retailFlower <- c("Usable Marijuana", "Marijuana Mix Package")
```

Retail flower types include: `r paste0(retailFlower, collapse="; ")`.

```{r}
# Production of ingredient, 3 time periods, KG, table

# Production of ingredient, 10 time periods, Units, chart
convChildT %>%
  group_by(year, month, inventorytype) %>%
  summarise(nConversions = sum(nConversions),
            childwt = sum(childwt),
            childusablewt = sum(childusablewt)) %>%
  filter(inventorytype%in%retailFlower,
         nConversions>1,
         !(year== 2017 & month ==11)) %>% # exclude nov 2017 (no data, just a few blips)
  ggplot(aes(x=month, y=nConversions/1e3, color=inventorytype)) +
  geom_line() + geom_point() +
  facet_grid(~year) +
  labs(title="Number of Ingredient Products Produced",
       y="1000 Conversions")

convChildT %>%
  group_by(year, month, inventorytype) %>%
  summarise(nConversions = sum(nConversions),
            childwt = sum(childwt),
            childusablewt = sum(childusablewt)) %>%
  filter(inventorytype%in%retailFlower,
         nConversions>1,
         !(year== 2017 & month ==11)) %>%
  ggplot(aes(x=month, y=childwt/1e3, color=inventorytype)) +
  geom_line() + geom_point() +
  facet_grid(~year) +
  labs(title="Weight of Ingredient Products Produced",
       y="weight (KG) Converted")

convChildT %>%
  group_by(year, month, inventorytype) %>%
  summarise(nConversions = sum(nConversions),
            childwt = sum(childwt),
            childusablewt = sum(childusablewt)) %>%
  filter(inventorytype%in%retailFlower,
         nConversions>1,
         !(year== 2017 & month ==11)) %>%
  ggplot(aes(x=month, y=childusablewt/1e3, color=inventorytype)) +
  geom_line() + geom_point() +
  facet_grid(~year) +
  labs(title="Usable weight of Ingredient Products Produced",
       y="Usable Weight (KG) Converted")
```

#### Retail, Non-Flower

```{r}
retailOther <- c("Solid Marijuana Infused Edible",
                 "Liquid Marijuana Infused Edible",
                 "Marijuana Extract for Inhalation",
                 "Marijuana Mix Infused",
                 "Capsule",
                 "Marijuana Infused Topicals",
                 "Tincture",
                 "Suppository")
```

Retail non-flower types include: `r paste0(retailOther, collapse="; ")`. 

```{r}
convChildT %>%
  filter(inventorytype%in%retailOther) %>%
  mutate(q = cut(month, c(0, 3.1, 6.1, 9.1, 12.1), labels=1:4),
         h = cut(month, c(0, 6.1, 12.1), labels=1:2),
         yearq = paste0(year,"-", q),
         yearh = paste0(year,"-", h)) %>%
  group_by(inventorytype, yearh) %>%
  summarise(KG = sum(childwt)/1e3) %>%
  spread(yearh, KG) %>%
  arrange(-`2017-1`) %>%
  filter(!is.na(`2016-2`)) %>%
  kable(digits=1, caption="Retail (non-flower) Production (KG) by 6-month period")


```

### 4C THC/CBD Concentrations

```{r}
potencyAnnual <- read_csv("../data/thccbdannual.csv")
```

#### Lots

```{r}
lots <- c("Flower Lot")

flowerLotPotency <- potencyAnnual %>% filter(invtype %in% lots)

# Display THC
flowerLotPotency %>% 
  select(-TotalCBD) %>%
  spread(invtype, TotalTHC) %>%
  kable(digits=1, caption='Ingredient Average THC Concentrations, by Year')

# Display CBD
flowerLotPotency %>% 
  select(-TotalTHC) %>%
  filter(test_year%in%2015:2017) %>%
  spread(invtype, TotalCBD) %>%
  kable(digits=2, caption='Average CBD %s')

```


#### "Ingredients"

First we compute the average THC/CBD concentrations for tests run in each year.  Note CBD was not tracked well in 2014/2015.

```{r}
# Display THC
potencyAnnual %>% 
  select(-TotalCBD) %>%
  filter(invtype %in% ingrdnts) %>%
  spread(invtype, TotalTHC) %>%
  kable(digits=1, caption='Ingredient Average THC Concentrations, by Year')

# Display CBD
potencyAnnual %>% 
  select(-TotalTHC) %>%
  filter(invtype %in% ingrdnts,
         test_year%in%2016:2017) %>%
  spread(invtype, TotalCBD) %>%
  kable(digits=2, caption='Average CBD %s')

```

Then, we may attempt to estimate MT THC/CBD produced, by multiplying each year's THC/CBD concentration by the weight of ingredient produced by year. But this is not currently possible, because we do not know the time cutoffs to analyze ingredient production by year. *TODO: Decide: should you simplify the MT estiamte or come with a workaround?*.

```{r getIngredientTHCMT}

```

#### Retail Products

Note: usableweight content for solid/liquid edibles is clearly wrong/too small. **To do: add estimated content for edibles to this table.** Also note that "usable marijuana" comes from flower lots, so potency for that should be equal to flower lots.

```{r}
# Estimate kgTHC for retail products (TotalTHC % * KG)
convChild %>%
  filter(inventorytype%in%c(retailOther, retailFlower)) %>%
  select(inventorytype, Units=childwt, G=childusablewt) %>%
  left_join(potencyAnnual %>%
               filter(test_year==2017) %>% select(-test_year),
             by=c('inventorytype'='invtype')) %>%
  mutate(kgTHC = G * TotalTHC / 1e6,
         kgCBD = G * TotalCBD / 1e6) %>%
  mutate(KG = G / 1e3,
         UnitsK = Units /1e3) %>% 
  ungroup %>%
  select(inventorytype, UnitsK, KG, THC=TotalTHC, CBD=TotalCBD, kgTHC, kgCBD) %>%
  arrange(-UnitsK) %>%
  kable(digits=1, caption="Retail Products: THC/CBD Concentrations and Weights")

# kgTHC over time? CANNOT DO THIS YET BC WE DON'T HAVE YEAR TAGS.
# convChildT10 %>%
#   filter(inventorytype%in%retailOther) %>%
#   select(inventorytype, Units=childweight, G=child_usableweight, rowN) %>%
#   left_join(potencyAnnual %>%
#                filter(test_year==2017) %>% select(-test_year),
#              by=c('inventorytype'='invtype')) %>%
#   mutate(kgTHC = G * TotalTHC / 1e6,
#          kgCBD = G * TotalCBD / 1e6) %>%
#   mutate(KG = G / 1e3,
#          UnitsK = Units /1e3) %>% 
#   ungroup %>%
#   select(inventorytype, UnitsK, KG, THC=TotalTHC, CBD=TotalCBD, kgTHC, kgCBD) %>%
#   arrange(-UnitsK) %>%
#   kable(digits=1, caption="Retail Products: THC/CBD Concentrations and Weights")
  
# NOTE: this does not work BC you're not joining tables correctly on "time" variable
# convChildT10 %>%
#   filter(inventorytype%in%retailOther) %>%
#   select(inventorytype, Units=childweight, G=child_usableweight, rowN) %>%
#   left_join(potencyAnnual %>%
#                filter(test_year==2017) %>% select(-test_year),
#              by=c('inventorytype'='invtype')) %>%
#   mutate(kgTHC = G * TotalTHC / 1e6,
#          kgCBD = G * TotalCBD / 1e6) %>%
#   mutate(KG = G / 1e3,
#          UnitsK = Units /1e3) %>% 
#   ggplot(aes(x=rowN, y=TotalTHC, color=inventorytype))+ geom_line()
  
```

### 4D. Farmgate revenue (by producer/processor good)

#### Plants/Harvest/Lotted Material (Producers)

This contains non-processed inputs.

#### TODO: add transfers divided by 3 time points for rows in tables?

```{r}
plants <- c("Seed", "Plant Tissue", "Mature Plant", "Clone", "Wet Flower")
lots <- c("Flower Lot", "Other Plant Material Lot")

transfers %>%
  filter(invtype %in% c(plants, lots)) %>% 
  arrange(-nTransfers) %>% select(-usableweight) %>% kable(digits=2)

transfersYr %>%
  filter(inventorytype %in%c(plants, lots)) %>%
  select(kUSD, year, inventorytype) %>%
  spread(inventorytype, kUSD) %>%
  kable(caption="$1000 sales", digits=1)

transfersYr %>%
  filter(inventorytype %in%c(plants, lots)) %>%
  select(units, year, inventorytype) %>%
  spread(inventorytype, units) %>%
  kable(caption="1000 units", digits=1)

transfersYr %>%
  filter(inventorytype %in%c(plants, lots)) %>%
  select(kg, year, inventorytype) %>%
  spread(inventorytype, kg) %>%
  kable(caption="kg", digits=1)

transfersYrMo %>%
  filter(inventorytype %in%c(plants, lots)) %>%
  ggplot(aes(x=month, y=units/1e3, color=inventorytype)) + geom_line() + facet_grid(~year) +
  labs(title="Plant and Lot Sales by Units (1000)")

transfersYrMo %>%
  filter(inventorytype %in%c(plants, lots)) %>%
  ggplot(aes(x=month, y=kUSD, color=inventorytype)) + geom_line() + facet_grid(~year) +
  labs(title="Plant and Lot Sales by $1000s")
```

####  (Processors)

This contains procesed inputs

```{r}
transfers %>%
  filter(invtype %in% ingrdnts) %>% arrange(-nTransfers) %>% select(-usableweight) %>% 
  kable(digits=2, caption="All-time production")

transfersYr %>%
  filter(inventorytype %in%ingrdnts) %>%
  select(kUSD, year, inventorytype) %>%
  spread(inventorytype, kUSD) %>%
  kable(caption="$1000 sales", digits=1)

transfersYr %>%
  filter(inventorytype %in%ingrdnts) %>%
  select(units, year, inventorytype) %>%
  spread(inventorytype, units) %>%
  kable(caption="1000 units", digits=1)

transfersYr %>%
  filter(inventorytype %in%ingrdnts) %>%
  select(kg, year, inventorytype) %>%
  spread(inventorytype, kg) %>%
  kable(caption="kg", digits=1)

transfersYrMo %>%
  filter(inventorytype %in%ingrdnts) %>%
  ggplot(aes(x=month, y=units/1e3, color=inventorytype)) + geom_line() +facet_grid(~year) +
  labs(title="Ingredient Sales by Units (1000)")

transfersYrMo %>%
  filter(inventorytype %in%ingrdnts) %>%
  ggplot(aes(x=month, y=kUSD, color=inventorytype)) + geom_line() + facet_grid(~year) +
  labs(title="Ingredient Sales by $1000s")

```

#### Retail Products

This examines only retail products.

```{r}
transfers %>%
  filter(invtype %in% c(retailFlower, retailOther)) %>% 
  mutate(pricePerG = saleprice/usableweight) %>%
  arrange(-nTransfers) %>% kable(digits=2, caption='All-time production')
```


```{r, fig.width=10}

transfersYr %>%
  filter(inventorytype %in% c(retailFlower, retailOther)) %>%
  arrange(-units) %>%
  select(year, inventorytype, unitsK) %>%
  spread(inventorytype, unitsK)%>% 
  kable(digits=2, caption='1000 units')

transfersYr %>%
  filter(inventorytype %in% c(retailFlower, retailOther)) %>%
  arrange(-kUSD) %>%
  select(year, inventorytype, kUSD) %>%
  spread(inventorytype, kUSD)%>% 
  kable(digits=2, caption='$1000s')

transfersYrMo %>%
  filter(inventorytype %in% c(retailFlower, retailOther)) %>%
  gather(metric, value, units, kg, kUSD) %>%
  filter(metric!='kg') %>%
  ggplot(aes(x=month, y=value, color=inventorytype)) + geom_line() +
  facet_grid(metric~year, scales='free') +
  labs(title="Retail Production: $, Units, Price-per-kg-usableweight") +
  theme_minimal()
  
```

### 4E. Retail Products

#### 4Ei: Sales: (Units, $) - by product type

##### Sales Volume (Units)

```{r, echo=FALSE}
# TODO: Update query for proper unit/item-transaction definition
# Chart
retailUSDxType %>%
  ggplot(aes(x=date, y=itemtransactions, color=invtype)) + geom_line() +
  labs(title="Retail Item-Transactions by Inventory Type",
       y="Item-transactions (retail data rows)",
       x="") +
  theme_minimal() +
  scale_x_date(date_labels = "%b '%y", date_breaks="6 months")


# Table - monthly
# retailUSDxType %>%
#   select(invtype, date, itemtransactions) %>%
#   spread(invtype, itemtransactions) %>%
#   knitr::kable(caption='Retail Item-Transactions By Inventory Type', digits=0)

# Table - annual
retailUSDxType %>%
  group_by(YEAR, invtype) %>%
  summarise(itemtransactions = sum(itemtransactions, na.rm=T)) %>%
  select(invtype, YEAR, itemtransactions) %>%
  spread(invtype, itemtransactions) %>%
  knitr::kable(caption='Retail Item-Transactions By Inventory Type - Annual', digits=0)

```

##### Sales Volume (Usable Weight)

Note: this is validated by tabulating usableweight sold in the retail table! (at least for usable MJ)

```{r, echo=FALSE}
# TODO: Update query for proper unit/item-transaction definition
# Chart
retailUSDxType %>%
  filter(usableweight >0 ) %>%
  ggplot(aes(x=date, y=usableweight/1e6, color=invtype)) + geom_line() +
  labs(title="Retail Item-Transactions by Inventory Type",
       y="usable weight (MT)",
       x="") +
  theme_minimal() +
  scale_x_date(date_labels = "%b '%y", date_breaks="6 months")


# Table - monthly
# retailUSDxType %>%
#   select(invtype, date, itemtransactions) %>%
#   spread(invtype, itemtransactions) %>%
#   knitr::kable(caption='Retail Item-Transactions By Inventory Type', digits=0)

# Table - annual
retailUSDxType %>%
  filter(usableweight >0 ) %>%
  group_by(YEAR, invtype) %>%
  summarise(usableweight = sum(usableweight, na.rm=T)/1e6) %>%
  select(invtype, YEAR, usableweight) %>%
  spread(YEAR, usableweight) %>%
  knitr::kable(caption='Usable Weight (MT) By Inventory Type - Annual', digits=2)
```

##### Sales Volume (Dollars)

```{r, echo=FALSE}
# Chart
retailUSDxType %>%
  ggplot(aes(x=date, y=price_x, color=invtype)) + geom_line() +
  labs(title="Gross Retail Sales by Inventory Type",
       y="$1000, Post-Excise",
       x="") +
  theme_minimal() +
  scale_x_date(date_labels = "%b '%y", date_breaks="6 months") +
  scale_y_continuous(labels=scales::dollar_format())


# Table
# retailUSDxType %>%
#   select(invtype, date, price_x) %>%
#   spread(invtype, price_x) %>%
#   knitr::kable(caption='Post-Excise Tax Sales By Inventory Type ($1k)', digits=0)


# Table - annual
retailUSDxType %>%
  group_by(YEAR, invtype) %>%
  summarise(price_x = sum(price_x)) %>%
  select(invtype, YEAR, price_x) %>%
  spread(invtype, price_x) %>%
  knitr::kable(caption='Post-Excise Tax Sales By Inventory Type ($1k) - Annual', digits=0)

```


#### 4Eii:THC/CBD Content

```{r load_edibles_thc, echo=F}
edible_thc <- read.csv("../data/THC_estimates_nocbddominantedibles.csv")
```

```{r, echo=FALSE}
edible_thc %>% 
  filter(str_detect(invtype, "Edible")) %>%
  ggplot(aes(x=month, y=kgTHC, fill=invtype)) +
  geom_col() + facet_grid(~year) +
  labs(title='Edbiles: kgTHC sold',
       caption="Counting THC-dominant edibles only")

edible_thc %>% ggplot(aes(x=month, y=kgTHC, fill=invtype)) +
  geom_col() + facet_grid(~year) +
  labs(title='kgTHC sold',
       caption="Counting THC-dominant edibles only")


# TODO: Update query for weighted averages
# Chart
retailUSDxType %>%
  ggplot(aes(x=date, y=totalTHC, color=invtype)) + geom_line() +
  labs(title="THC Content by Inventory Type",
       y="THC Percent",
       x="") +
  theme_minimal() +
  scale_x_date(date_labels = "%b '%y", date_breaks="6 months")


# Table
# retailUSDxType %>%
#   select(invtype, date, totalTHC) %>%
#   spread(invtype, totalTHC) %>%
#   knitr::kable(caption='Mean THC Content By Inventory Type', digits=0)

retailUSDxType %>%
  group_by(YEAR, invtype) %>%
  summarise(totalTHC = weighted.mean(totalTHC, price_x)) %>%
  select(invtype, YEAR, totalTHC) %>%
  spread(invtype, totalTHC) %>%
  knitr::kable(caption='Mean THC Content By Inventory Type (Weighted by $ Sales) - Annual', digits=1)

```

##### Edibles Only



```{r, echo=FALSE}
# TODO: Update query for weighted averages
# Chart
retailUSDxType %>%
  ggplot(aes(x=date, y=totalCBD, color=invtype)) + geom_line() +
  labs(title="CBD Content by Inventory Type",
       y="CBD Percent",
       x="") +
  theme_minimal() +
  scale_x_date(date_labels = "%b '%y", date_breaks="6 months")


# Table
# retailUSDxType %>%
#   select(invtype, date, totalCBD) %>%
#   spread(invtype, totalCBD) %>%
#   knitr::kable(caption='Mean CBD Content By Inventory Type', digits=0)

retailUSDxType %>%
  group_by(YEAR, invtype) %>%
  summarise(totalCBD = weighted.mean(totalCBD, price_x)) %>%
  select(invtype, YEAR, totalCBD) %>%
  spread(invtype, totalCBD) %>%
  knitr::kable(caption='Mean CBD Content By Inventory Type (Weighted by $ Sales) - Annual', digits=1)

```

### 4F. Supply Chain Dynamics: Product Flows and Conversion Ratios

** TODO: Add analysis from the pathways document?**

##### 4Fi.	Efficiency: Flower/OPM-per-ingredient (gram-to-gram ratio). Conversion Ratios (inventoryconversions)

This data needs substantial cleaning (top-censoring the parent and child weights; allowing usablewt to be interpretable by performing the correct wt*usableweight calculations (perhaps also requiring top-coding or some other conditional logic to prevent absurd values)) before it can be interpretable.

```{r}
# TODO: clean childusableweight when it an childwt is present.
ratiosRaw <- convDetailed %>%
  group_by(parent, child) %>%
  summarise(conversions = sum(nConversions),
            ratiowt2wt = sum(parentwt, na.rm=T)/sum(childwt, na.rm=T),
            ratiowt2uwt = sum(parentwt, na.rm=T)/sum(childusablewt, na.rm=T),
            ttlparentwt = sum(parentwt, na.rm=T),
            ttlchildwt = sum(childwt, na.rm=T),
            ttlchilduwt = sum(childusablewt, na.rm=T),
            # ttlchildwtXuwt = sum(childwt*childusablewt, na.rm=T),
            ratiowt2wtXuwt = sum(parentwt, na.rm=T)/sum(childusablewt * childwt, na.rm=T)
            ) %>%
  arrange(-conversions)

kable(ratiosRaw, digits=2)
```

###### (wet?) Flower / OPM – to –  ingredient… (Hydrocarbon wax; CO2 Hash Oil;  Food Grade Solvent Extract)...

###### Flower / OPM – to – final product (Extract, Solid / Liquid Edible, etc.)



##### 4Fii. End products as share of canopy:

#### Conversion Pathway Prevalence

The table below produces a simple count of the number of records in each.

```{r}
convPaths %>% head(50) %>% kable(caption="Dominant Conversion Pathways")
```

[[ compute pathway prevalence in percentage terms, a la Markov chain, and put results here ]]


###### Retail products by % of flower/OPM production (by weight)

###### by % of “all” production


### Licensee Revenue Analysis

#### Producer/P&P/Processors

This can be generated from inventorytransfers table. inventorytransfer::saleprice. Validate/verify this. (5.3mil records)


```{r}
# GoogleQuery: ?????

# Aggregate revenues for all producers.

```

#### Stores

This can be generated from the dispensing table.


### Harvest

[[ Results will go here ]]  
[[ kg harvest of wet flower, dry flower, OPM, and waste]] 

And the 5 most popular child products (data needs cleaning):

```{r}
convDetailed %>%
  filter(!child %in% c("Marijuana Mix", "Flower Lot", "Other Plant Material Lot"),
         !child %in% c("Usable Marijuana")) %>%
  group_by(child) %>%
  summarise(nConversions = sum(nConversions),
           childwt = sum(childwt, na.rm=T),
           childusablewt = sum(childusablewt, na.rm=T)) %>%
  arrange(-childwt) %>%
  head(5) %>%
  kable(caption='inventoryconversion children')
```

Though it is less interesting, we can also tabulate data by parent type. This can be used to validate.

 
```{r, eval = F, include=F}
# Queries


# QUERY: Get weight of harvested material. This crashes Google Query.
SELECT location, plantid, MIN(sessiontime) AS firstharvest,
SUM(CASE WHEN inventorytype = 29 THEN dweight else 0 END) as wet_weight,
SUM(CASE WHEN inventorytype = 6 THEN dweight else 0 END) as dry_weight,
SUM(CASE WHEN inventorytype = 9 THEN dweight else 0 END) as opm_weight
FROM [rand-systems:full_WA_data__proper.biotrackthc_plantderivatives]
-- remove deleted records
WHERE deleted = 0
GROUP BY location, plantid, inventorytype;

# SIMPLER (Crash-proof?): Get weight of harvested material.
SELECT location,
SUM(CASE WHEN inventorytype = 29 THEN dweight else 0 END) as wet_weight,
SUM(CASE WHEN inventorytype = 6 THEN dweight else 0 END) as dry_weight,
SUM(CASE WHEN inventorytype = 9 THEN dweight else 0 END) as opm_weight
FROM [rand-systems:full_WA_data__proper.biotrackthc_plantderivatives]
-- remove deleted records
WHERE deleted = 0
GROUP BY location, inventorytype;

# RUN THIS QUERY

# This query is saved in the table: plant_stats_distinct_location
# select a.location AS location, b.locationtype AS locationtype, a.plantid AS plantid,
# a.sessiontime AS sessiontime, a.wet_weight AS wet_weight, a.dry_weight AS dry_weight,
# a.opm_weight AS opm_weight
# from [rand-systems:TEAM_WORKSPACE_USE_ME.plant_stats_distinct] a
# JOIN (
# select id, locationtype
# FROM
# [rand-systems:full_WA_data__proper.biotrackthc_locations]) b ON a.location =b.id
# WHERE b.locationtype < 7;
```

#### Production Volumes

### Processing / Manufacturing

This sub-section includes: 1) production volumes, 2) pathway prevalence, 3) conversion ratios



## Appendix

### Validation

We can check usable weight v weight tables in retail and inventoryconversions.

+ Spike in usable marijuana production early 2017 by usableweight. Fixed by top-coding usable marijuana uw:w ratio @ 1 ounce.
+ spike in MJ mix for usable weight.

```{r, eval = F}
# USE THIS SCRIPT TO DETECT AND TOPCODE OUTLIERS  (i.e. for histograms with outliers)
convChildT %>%
  mutate(ratio=childusablewt/childwt) %>%
  ggplot() + geom_histogram(aes(x=ratio, fill=inventorytype)) + facet_wrap(~inventorytype, scales='free')

# View in table
convChildT %>%
  # filter(inventorytype == "Marijuana Mix") %>%
  arrange(-uwper) #%>%
  group_by(year, month, inventorytype) %>%
  summarise(nConversions = sum(nConversions),
            childwt = sum(childwt),
            childusablewt = sum(childusablewt),
            ratio = childusablewt/childwt)
  
convChildT %>%
  filter(inventorytype == "Marijuana Mix") %>%
  mutate(wtper = childwt / nConversions) %>%
  arrange(-wtper) #%>%
  group_by(year, month, inventorytype) %>%
  summarise(nConversions = sum(nConversions),
            childwt = sum(childwt),
            childusablewt = sum(childusablewt),
            ratio = childusablewt/childwt)
  
```

### Ingredient Production (reliable?)

TODO: validate usableweight and weight. Weight appears to indicate literal weight. Usableweight must be miscoded, as it is >> weight.

```{r}
# TODO: clean childwt to remove outliers. Currently you have way too much childwt going to Extract for Inhalation and nConversions!

# Production of ingredient, 10 time periods, Units, chart
convChildT %>%
  group_by(year, month, inventorytype) %>%
  summarise(nConversions = sum(nConversions),
            childwt = sum(childwt),
            childusablewt = sum(childusablewt)) %>%
  filter(inventorytype%in%ingrdnts,
         nConversions>1,
         (year!= 2017 & month !=11)) %>%
  ggplot(aes(x=month, y=nConversions/1e3, color=inventorytype)) +
  geom_line() + geom_point() +
  facet_grid(~year) +
  labs(title="Ingredient Products Produced",
       y="1000 Conversions")

convChildT %>%
  group_by(year, month, inventorytype) %>%
  summarise(nConversions = sum(nConversions),
            childwt = sum(childwt),
            childusablewt = sum(childusablewt)) %>%
  filter(inventorytype%in%ingrdnts,
         nConversions>1,
         (year!= 2017 & month !=11)) %>%
  ggplot(aes(x=month, y=childwt/1e3, color=inventorytype)) +
  geom_line() + geom_point() +
  facet_grid(~year) +
  labs(title="Weight of Ingredient Products Produced",
       y="weight (KG) Converted")

convChildT %>%
  group_by(year, month, inventorytype) %>%
  summarise(nConversions = sum(nConversions),
            childwt = sum(childwt),
            childusablewt = sum(childusablewt)) %>%
  filter(inventorytype%in%ingrdnts,
         nConversions>1,
         (year!= 2017 & month !=11)) %>%
  ggplot(aes(x=month, y=childusablewt/1e3, color=inventorytype)) +
  geom_line() + geom_point() +
  facet_grid(~year) +
  labs(title="Usable weight of Ingredient Products Produced -- PROB NOT RELIABLE",
       y="Usable Weight (KG) Converted")


# summary table: show kg produced by year-quarter
convChildT %>%
  filter(inventorytype%in%ingrdnts) %>%
  mutate(q = cut(month, c(0, 3.1, 6.1, 9.1, 12.1), labels=1:4),
         h = cut(month, c(0, 6.1, 12.1), labels=1:2),
         yearq = paste0(year,"-", q),
         yearh = paste0(year,"-", h)) %>%
  group_by(inventorytype, yearh) %>%
  summarise(KG = sum(childusablewt)/1e3) %>%
  spread(yearh, KG) %>%
  arrange(-`2017-1`) %>%
  filter(!is.na(`2016-2`)) %>%
  kable(digits=1, caption="Ingredient Production (KG) by 6-month period")

```

### Retail production

TODO: find out how to interpret weight v usable weight!!! These are bullshit. You need to go into the tables and figure out what is what.

```{r}


# Production of ingredient, 10 time periods, Units, chart
convChildT %>%
  group_by(year, month, inventorytype) %>%
  summarise(nConversions = sum(nConversions),
            childwt = sum(childwt),
            childusablewt = sum(childusablewt)) %>%
  filter(inventorytype%in%retailOther,
         nConversions>1,
         (year!= 2017 & month !=11)) %>%
  ggplot(aes(x=month, y=nConversions/1e3, color=inventorytype)) +
  geom_line() + geom_point() +
  facet_grid(~year) +
  labs(title="Number of Ingredient Products Produced",
       y="1000 Conversions")

convChildT %>%
  group_by(year, month, inventorytype) %>%
  summarise(nConversions = sum(nConversions),
            childwt = sum(childwt),
            childusablewt = sum(childusablewt)) %>%
  filter(inventorytype%in%retailOther,
         nConversions>1,
         (year!= 2017 & month !=11)) %>%
  ggplot(aes(x=month, y=childwt/1e3, color=inventorytype)) +
  geom_line() + geom_point() +
  facet_grid(~year) +
  labs(title="Weight of Ingredient Products Produced",
       y="weight (KG) Converted")

convChildT %>%
  group_by(year, month, inventorytype) %>%
  summarise(nConversions = sum(nConversions),
            childwt = sum(childwt),
            childusablewt = sum(childusablewt)) %>%
  filter(inventorytype%in%retailOther,
         nConversions>1,
         (year!= 2017 & month !=11)) %>%
  ggplot(aes(x=month, y=childusablewt/1e3, color=inventorytype)) +
  geom_line() + geom_point() +
  facet_grid(~year) +
  labs(title="Usable weight of Ingredient Products Produced",
       y="Usable Weight (KG) Converted")
```

## Notes on workflow / tables

### plantderivatives (Harvest Events)

The "plantderivatives" table records the harvesting from plants of dry flower, wet flower, other plant material, and waste. Aggregations are calculated by adding **dweight** after cleaning, top-censored based on harvest-per-plant (at 1.5kg each **?**). **dwholeweight** records the entire harvest weight across many plants; **dweight** apportions an equal fraction of this across all plants harvested. 

**Notes**

+ inventory::waste record count: 989,387 
+ sum(inventory::waste[inventorytype==26]) > 600mil kg (assuming units = gram)
+ Almost all dry flower has inventoryid. Many plants have a wet weight but no dry weight, e.g. 250,000 plants in November 2017 due to end of traceability reporting.


### inventorycombinations (Lotting Events)

The "inventorycombinations" table records the combination of individual raw production units to aggregate lots.  The input types to this process are Dry Flower (inventorytype 6) and Other Plant Material (9). Lotted units include Flower lot (13), OPM lot (14), and marijuana mix (30). I speculate that inventorycombinations is essentially inventoryconversions but for same-type converrsions (e.g. flower lot - flower lot), as most entries have an NA parent-type and only an inventorytype for children. There are a few entries with different-type conversions, but these are likely errors.

TODOs

+ Verify understanding that table captures all same-type conversions (i.e. combinations), and this explains why often oldtype = NA.
+ Data cleaning: Quantities of the parent ("parent_difference") and child ("childweight", "child_usableweight"). Top-censor values, e.g., at 99%ile by parent/child inventorytype.
+ very regulations to verify max parent lot sizes (5kg flower lot /10kg OPM lost).

```{r}
# TODO: after parsing SESSIONTIME, add year-month to query.
# Query (lotQuery): simple count of lots
# -- Count the number of lots made (by input/output type) over time, statewide
# SELECT OLDTYPE, NEWTYPE, count(*) as numlots
# FROM [full_WA_data__proper.biotrackthc_inventorycombinations]
# GROUP BY oldtype, newtype

lots <- read_csv("../gqoutput/results-20180630-122340.csv") %>%
  mutate(OLDTYPE = getInvtype(OLDTYPE),
         NEWTYPE = getInvtype(NEWTYPE)
         )
knitr::kable(lots, caption="Lot counts by input-output type")
```

### inventorytransfers (Wholesale Transactions)

This table records all licensee-to-licensee transactions. Because the inventory transfers table has a redacted date field, we supplement it with date information merged from the "inventory" table. This provides an estimate for dates of transfers.


### inventoryconversions (Processing and Manufacturing)

The inventory conversions table records all conversions from one inventory type to another. This is key. This table is tagged with a serial ID (allowing **time-series**) and **licensee-level** data (manufacturer of the child product), so complex analysis is possible. By merging on inventoryid, products downstream of testing can also have **THC** contents estimated. By merging with the table inventorytransfers, we ought to be able to compute all **revenue** figures too.  Data span nearly the entire supply chain:

+ Lotting stage (flower -> flower lot)
+ processing/manufacturing stage 1 (flower/OPM to intermediate extracts)
+ processing/manufacturing stage 1 (intermediate extracts to retail product)

This table gets the finest grain of stuff (licensee x parent-type x child-type). Should also add date once we know how to parse that.

**Available information in this table**  
date, location, parentweight (always grams?), childweight, childusableweight.


TODOs:

+ Add this table to the new Google Query schema ("...proper")
+ clean childusableweight when it an childwt is present. it seems like we sometimes but not always have to multiply wt * usablewt. Until we do that, the ratios will be wrong. 
+ Enrich inventoryconversions table with **THC** (merge on inventoryid with lab table, for eligible products).
+ Since data is tagged only with creator license, but since it seems like this table captures all conversion pathways, many products are re-appearing in this table several times. So, attempt to create a new table that wouldu use a recursive merge to analyze with to/from licensee data? (e.g. for network analysis)

Below we produce a preview of the data in this table. (Date is also available but not shown here.)

```{r}
kable(convDetailed %>% head(5))
#        dplyr::sample_n(5))
```

This table can be viewed with respect to parent or child products. Parent products include lots and all intermediate products. Child products include all intermediate products and retail products.  

Below we show the five most popular parent products (data needs cleaning):


```{r}
convDetailed %>%
  filter(!parent %in% c("Marijuana Mix", "Flower Lot", "Other Plant Material Lot"),
         !parent %in% c("Usable Marijuana")) %>%
  group_by(parent) %>%
  summarise(nConversions = sum(nConversions),
           parentwt = sum(parentwt, na.rm=T)) %>%
  arrange(-parentwt) %>%
  head(5) %>%
  kable(caption='inventoryconversion parents')
```

## Validation

Here are miscellaneous tables.

### Audit harvest v lots v conversion-parents

Lots are produced in the inventorycombinations table (from dry flower or OPM), before they then re-appear in the inventoryconversions table for conversions to other products. Therefore we can use these two tables (after cleaning) to validate the data. We will triangulate this from various tables:

+ inventorycombinations - lotting
+ inventoryconversions - parent product
+ inventoryconversions - child product

```{r}
lots %>% 
  group_by(NEWTYPE) %>%
  summarise(numlots = sum(numlots)) %>%
  kable(caption="Number of lots from inventorycombinations")
```

```{r}
# Plot kg weight
convDetailedT %>%
  filter(parent %in% c("Marijuana Mix", "Flower Lot", "Other Plant Material Lot"),
         (year != 2017 & month !=11)) %>%
  group_by(parent, month, year) %>%
  summarise(nConversions = sum(nConversions),
           parentwt = sum(parentwt, na.rm=T)) %>%
  ggplot(aes(x=month, y=parentwt/1e6, color=parent)) + 
  facet_grid(~year) +
  geom_point() + geom_line() +
  labs(y="kg weight", title="Production of Lots / Mix",
       subtitle="types appear as parents in conversion table")

# Chart # Conversions
# convDetailedT %>%
#   filter(parent %in% c("Marijuana Mix", "Flower Lot", "Other Plant Material Lot"),
#          (year != 2017 & month !=11)) %>%
#   group_by(parent, month, year) %>%
#   summarise(nConversions = sum(nConversions),
#            parentwt = sum(parentwt, na.rm=T)) %>%
#   ggplot(aes(x=month, y=nConversions/1e3, color=parent)) + 
#   facet_grid(~year) +
#   geom_point() + geom_line() +
#   labs(y="thousand conversions", title="Production of Lots / Mix")

```

```{r}
convDetailedT %>%
  filter(child %in% c("Marijuana Mix", "Flower Lot", "Other Plant Material Lot"),
         (year != 2017 & month !=11)) %>%
  group_by(child, month, year) %>%
  summarise(nConversions = sum(nConversions),
           childwt = sum(childwt, na.rm=T),
           childusablewt = sum(childusablewt, na.rm=T)) %>%
  ggplot(aes(x=month, y=childwt/1e6, color=child)) + 
  facet_grid(~year) +
  geom_point() + geom_line() +
  labs(y="MT weight", title="Production FROM Lots / Mix",
       subtitle="types appear as children in conversion table")


convDetailedT %>%
  filter(child %in% c("Marijuana Mix", "Flower Lot", "Other Plant Material Lot"),
         (year != 2017 & month !=11)) %>%
  group_by(child, month, year) %>%
  summarise(nConversions = sum(nConversions),
           childwt = sum(childwt, na.rm=T),
           childusablewt = sum(childusablewt, na.rm=T)) %>%
  ggplot(aes(x=month, y=childusablewt/1e6, color=child)) + 
  facet_grid(~year) +
  geom_point() + geom_line() +
  labs(y="MT usable weight", title="Production FROM Lots / Mix",
       subtitle="types appear as children in conversion table")

convDetailedT %>%
  filter(child %in% c("Marijuana Mix", "Flower Lot", "Other Plant Material Lot"),
         (year != 2017 & month !=11)) %>%
  group_by(child, month, year) %>%
  summarise(nConversions = sum(nConversions),
           childwt = sum(childwt, na.rm=T),
           childusablewt = sum(childusablewt, na.rm=T)) %>%
  ggplot(aes(x=month, y=nConversions/1e3, color=child)) + 
  facet_grid(~year) +
  geom_point() + geom_line() +
  labs(y="thousand conversions", title="Production FROM Lots / Mix",
       subtitle="types appear as children in conversion table")


```

Though it is less interesting, we can also tabulate data by parent type. This can be used to validate.

### Validate Conversion-parents

This is not intrinsically interesting but could be used to validate harvest/lotting data. Note an average conversion-weight of almost 5000 (5kg?) for flower and 10,000 (10kg?) for OPM.

```{r}
knitr::kable(convParent, digits=1)
```