---
title: "Traceability-Based Findings v 1.4"
author: "Steven Davenport"
date: "`r format(Sys.time(), '%B %d, %Y (%H:%M)')`"
output: html_document
---

**Version history**

v1.4 (July 3) Restructured outline; sent to JPC/BK for review.
v1.3 (June 30) restructured outline.  
v1.2 (June 30) added analysis of inventoryconversions table.  
v1.1 (June 29) clarified outline; incorporated comments from Kee Won RE methods. Was sent briefly to JPC.  
v1.0 (June 27) provided outline; finished first draft of retail tables.

## Introduction

This report is an iterative document generated by RMarkdown. This document consolidates findings related to the WA traceability data. Queries are performed in Google Query, for export to CSVs that are loaded and cleaned in this script for display/plotting. It proceeds in several major parts:

1. Report outline
2. Notes on table (previews, ToDos, and methodological notes)
3. Results
4. Other output used to validate data.

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      # Graphic output
                      fig.width = 8, fig.align='center')
library(tidyverse)
library(knitr)
source("functions.r")
#TODO: write function to turn inventorytype to invtype
```

## Report Outline

This structure follows product as it moves down the supply chain, from harvest to sale. Sections are divided accordingly. By default, I assume these pulls will be done by year, or year-month, or year-licensee. It is not directly clear from the project description whether the LCB is interested in these computations in aggregate over-time, or across all time periods but comparing licensees, or a combination/interaction of both.


+ Harvest Events (tbl:plantderivatives)
  + Primary data pulls:
    + Wet Flower: kg harvested
    + Other Plant Material: kg harvested
    + Dry Flower: kg harvested/cured
    + Waste: kg wasted
  + Cleaning:
    + top-censor per-plant harvest
  + Secondary data analysis:
    + totals by year, licensee
+ Lotting Events (tbl: inventorycombinations)
  + Primary:
    + Flower Lot: kg produced (from (dry) flower)
    + OPM Lot: kg produced (from OPM)
    + Marijuana Mix: kg produced (from *??*)
  + Cleaning:
    + top-censor per-combination values
  + Secondary:
    + Compare per-licensee harvest v lotting (ID wasters/cheaters)
+ Processing / Manufacturing Events (tbl: inventoryconversions)
  + Primary:
    + Production Volumes
      + Of each intermediate product (grams) *(all products?)*
    + Prevalence of conversion pathways *(simplify so we dont have to compute all pathways?)*
      + lot -> intermediate product (int)
      + int. -> int.
      + int. -> retail
    + Conversion ratios (grams-to-grams) of each pathway
  + Cleaning:
    + top-censor parent and child quantities per conversion
  + Secondary:
    + Examine conversion ratios per-licensee? (ID wasters/cheaters)
    + Examine market concentration: 
  + Generate a Lorenz curve / HHI for each parent/child product type? Perhaps separate for each year? This can let us analyze 
  + Make Markov-type matrix of conversion pathways?
+ Retail Events (tbl: dispensing)
  + Sales volume by retail product type (Units, $, g (where applicable)):
    + Usable Marijuana; Marijuana Mix Infused; Marijuna Mix Package; etc.
  + THC Content and trends
    + Usable Marijuana; Marijuana Mix Infused; Marijuana Mix Package; etc.
+ Licensee-level (tbl: inventorytransfers) *(pending dates, requested from LCB)*
  + Primary:
    + Revenues by Licensee, License Class: Producer; P/P; Processor/ Retailer
  + Cleaning:
    + top-censor
  + Secondary:
    + Examine market-concentration. Calculate firm-marketshare/HHI/Lorenz Curve for each product type? Change over time?

  

## Notes on workflow / tables

### plantderivatives (Harvest Events)

The "plantderivatives" table records the harvesting from plants of dry flower, wet flower, other plant material, and waste. Aggregations are calculated by adding **dweight** after cleaning, top-censored based on harvest-per-plant (at 1.5kg each **?**). **dwholeweight** records the entire harvest weight across many plants; **dweight** apportions an equal fraction of this across all plants harvested. 

**Notes**

+ inventory::waste record count: 989,387 
+ sum(inventory::waste[inventorytype==26]) > 600mil kg (assuming units = gram)
+ Almost all dry flower has inventoryid. Many plants have a wet weight but no dry weight, e.g. 250,000 plants in November 2017 due to end of traceability reporting.


### inventorycombinations (Lotting Events)

The "inventorycombinations" table records the combination of individual raw production units to aggregate lots.  The input types to this process are Dry Flower (inventorytype 6) and Other Plant Material (9). Lotted units include Flower lot (13), OPM lot (14), and marijuana mix (30). I speculate that inventorycombinations is essentially inventoryconversions but for same-type converrsions (e.g. flower lot - flower lot), as most entries have an NA parent-type and only an inventorytype for children. There are a few entries with different-type conversions, but these are likely errors.

TODOs

+ Verify understanding that table captures all same-type conversions (i.e. combinations), and this explains why often oldtype = NA.
+ Data cleaning: Quantities of the parent ("parent_difference") and child ("childweight", "child_usableweight"). Top-censor values, e.g., at 99%ile by parent/child inventorytype.
+ very regulations to verify max parent lot sizes (5kg flower lot /10kg OPM lost).

```{r}
# TODO: after parsing SESSIONTIME, add year-month to query.
# Query (lotQuery): simple count of lots
# -- Count the number of lots made (by input/output type) over time, statewide
# SELECT OLDTYPE, NEWTYPE, count(*) as numlots
# FROM [full_WA_data__proper.biotrackthc_inventorycombinations]
# GROUP BY oldtype, newtype
lots <- read_csv("../gqoutput/results-20180630-122340.csv") %>%
  mutate(OLDTYPE = getInvtype(OLDTYPE),
         NEWTYPE = getInvtype(NEWTYPE)
         )
knitr::kable(lots, caption="Lot counts by input-output type")
```

### inventorytransfers (Wholesale Transactions)

This table records all licensee-to-licensee transactions, including a **price** but not date. This table cannot be instantly enriched with THC data, but perhaps could if additional merging is performed as to link inventoryids with inventoryparentids.


### inventoryconversions (Processing and Manufacturing)

The inventory conversions table records all conversions from one inventory type to another. This is key. This table is tagged with (allowing **time-series**) and **licensee-level** data (manufacturer of the child product), so complex analysis is possible. By merging on inventoryid, products downstream of testing can also have **THC** contents estimated. By merging with the table inventorytransfers, we ought to be able to compute all **revenue** figures too. Data span nearly the entire supply chain:

+ Lotting stage (flower -> flower lot)
+ processing/manufacturing stage 1 (flower/OPM to intermediate extracts)
+ processing/manufacturing stage 1 (intermediate extracts to retail product)

This table gets the finest grain of stuff (licensee x parent-type x child-type). Should also add date once we know how to parse that.

**Available information in this table**  
date, location, parentweight (always grams?), childweight, childusableweight.


TODOs:

+ Add this table to the new Google Query schema ("...proper")
+ clean childusableweight when it an childwt is present. it seems like we sometimes but not always have to multiply wt * usablewt. Until we do that, the ratios will be wrong. 
+ Enrich inventoryconversions table with **THC** (merge on inventoryid with lab table, for eligible products).
+ Since data is tagged only with creator license, but since it seems like this table captures all conversion pathways, many products are re-appearing in this table several times. So, attempt to create a new table that wouldu use a recursive merge to analyze with to/from licensee data? (e.g. for network analysis)

Below we produce a preview of the data in this table. (Date is also available but not shown here.)

```{r}
# -- QUERY
#  SELECT inventorytype, inventorytype_parent, location,
#    count(*) as nConversions,
#    sum(CAST(parent_difference as integer)) as parentwt,
#    sum(CAST(childweight as integer)) as childwt,
#    sum(CAST(child_usableweight as integer)) as childusablewt
# FROM [full_WA_data.biotrackthc_inventoryconversions]
# GROUP BY inventorytype, inventorytype_parent, location

convDetailed <- read_csv("../gqoutput/results-20180630-133936.csv") %>%
  mutate(parent = getInvtype(inventorytype_parent),
         child = getInvtype(inventorytype))  %>%
  select(-inventorytype_parent, -inventorytype) %>%
  arrange(-nConversions)

kable(convDetailed %>% 
        sample_n(5))

# TODO: Add licensee name, date
write.csv(convDetailed, "../output/conversionsDetailed.csv")

```

This table can be viewed with respect to parent or child products. Parent products include lots and all intermediate products. Child products include all intermediate products and retail products.  

Below we show the five most popular parent products (data needs cleaning):


```{r}
convDetailed %>%
  filter(!parent %in% c("Marijuana Mix", "Flower Lot", "Other Plant Material Lot"),
         !parent %in% c("Usable Marijuana")) %>%
  group_by(parent) %>%
  summarise(nConversions = sum(nConversions),
           parentwt = sum(parentwt, na.rm=T)) %>%
  arrange(-parentwt) %>%
  head(5) %>%
  kable(caption='inventoryconversion parents')
```

And the 5 most popular child products (data needs cleaning):

```{r}
convDetailed %>%
  filter(!child %in% c("Marijuana Mix", "Flower Lot", "Other Plant Material Lot"),
         !child %in% c("Usable Marijuana")) %>%
  group_by(child) %>%
  summarise(nConversions = sum(nConversions),
           childwt = sum(childwt, na.rm=T),
           childusablewt = sum(childusablewt, na.rm=T)) %>%
  arrange(-childwt) %>%
  head(5) %>%
  kable(caption='inventoryconversion children')
```

Though it is less interesting, we can also tabulate data by parent type. This can be used to validate.


## Results

### Harvest

[[ Results will go here ]]  
[[ kg harvest of wet flower, dry flower, OPM, and waste]] 

 
```{r, eval = F, include=F}
# Queries


# QUERY: Get weight of harvested material. This crashes Google Query.
SELECT location, plantid, MIN(sessiontime) AS firstharvest,
SUM(CASE WHEN inventorytype = 29 THEN dweight else 0 END) as wet_weight,
SUM(CASE WHEN inventorytype = 6 THEN dweight else 0 END) as dry_weight,
SUM(CASE WHEN inventorytype = 9 THEN dweight else 0 END) as opm_weight
FROM [rand-systems:full_WA_data__proper.biotrackthc_plantderivatives]
-- remove deleted records
WHERE deleted = 0
GROUP BY location, plantid, inventorytype;

# SIMPLER (Crash-proof?): Get weight of harvested material.
SELECT location,
SUM(CASE WHEN inventorytype = 29 THEN dweight else 0 END) as wet_weight,
SUM(CASE WHEN inventorytype = 6 THEN dweight else 0 END) as dry_weight,
SUM(CASE WHEN inventorytype = 9 THEN dweight else 0 END) as opm_weight
FROM [rand-systems:full_WA_data__proper.biotrackthc_plantderivatives]
-- remove deleted records
WHERE deleted = 0
GROUP BY location, inventorytype;

# RUN THIS QUERY

# This query is saved in the table: plant_stats_distinct_location
# select a.location AS location, b.locationtype AS locationtype, a.plantid AS plantid,
# a.sessiontime AS sessiontime, a.wet_weight AS wet_weight, a.dry_weight AS dry_weight,
# a.opm_weight AS opm_weight
# from [rand-systems:TEAM_WORKSPACE_USE_ME.plant_stats_distinct] a
# JOIN (
# select id, locationtype
# FROM
# [rand-systems:full_WA_data__proper.biotrackthc_locations]) b ON a.location =b.id
# WHERE b.locationtype < 7;
```

### Lotting

[[ Results will go here ]]  
[[ kg harvest of flower lot, opm lot, marijuana mix]] 


### Processing / Manufacturing

This sub-section includes: 1) production volumes, 2) pathway prevalence, 3) conversion ratios

#### Production Volumes

```{r}
convChild <- read_csv("../gqoutput/results-20180630-131250.csv") %>%
  mutate(inventorytype = getInvtype(inventorytype),
         wtPer = childwt/nConversions,
         usablewtPer = childusablewt/nConversions)  %>%
  arrange(-childwt)
# -- QUERY: CHILD WEIGHTS.
#  SELECT inventorytype,
#    count(*) as nConversions,
#    sum(CAST(childweight as integer)) as childwt,
#    sum(CAST(child_usableweight as integer)) as childusablewt
# FROM [full_WA_data.biotrackthc_inventoryconversions]
# GROUP BY inventorytype

knitr::kable(convChild, digits=0)
```

#### Conversion Pathway Prevalence

The table below produces a simple count of the number of records in each.

```{r}
convPaths <- read_csv("../gqoutput/results-20180630-124915.csv") %>%
  mutate(parent = getInvtype(inventorytype_parent),
         child = getInvtype(inventorytype))  %>%
  select(parent, child, nConversions) %>%
  arrange(-nConversions)
# -- Inventory Conversion parent-child
# SELECT inventorytype, inventorytype_parent, count(*) as nConversions
# FROM [full_WA_data.biotrackthc_inventoryconversions]
# GROUP BY inventorytype, inventorytype_parent
convPaths %>% head(50) %>% kable(caption="Dominant Conversion Pathways")
```

[[ compute pathway prevalence in percentage terms, a la Markov chain, and put results here ]]


#### Conversion Ratios (inventoryconversions)

This data needs substantial cleaning (top-censoring the parent and child weights; allowing usablewt to be interpretable by performing the correct wt*usableweight calculations (perhaps also requiring top-coding or some other conditional logic to prevent absurd values)) before it can be interpretable.

```{r}
options(scipen=99)
# TODO: clean childusableweight when it an childwt is present.
ratiosRaw <- convDetailed %>%
  group_by(parent, child) %>%
  summarise(conversions = sum(nConversions),
            ratiowt2wt = sum(parentwt, na.rm=T)/sum(childwt, na.rm=T),
            ratiowt2uwt = sum(parentwt, na.rm=T)/sum(childusablewt, na.rm=T),
            ttlparentwt = sum(parentwt, na.rm=T),
            ttlchildwt = sum(childwt, na.rm=T),
            ttlchilduwt = sum(childusablewt, na.rm=T),
            # ttlchildwtXuwt = sum(childwt*childusablewt, na.rm=T),
            ratiowt2wtXuwt = sum(parentwt, na.rm=T)/sum(childusablewt * childwt, na.rm=T)
            ) %>%
  arrange(-conversions)

kable(ratiosRaw)
```

### Retail Products

```{r, retailVolume}
# GoogleQuery: RetailUSDxType
# TODO: replace this query with the saved version? (it was lost?)

# SELECT invtype, 
# YEAR(sale_time) as YEAR,
# MONTH(sale_time) as MONTH,
# -- number of rows (item-transactions)
# count(*) as itemtransactions,
# sum(price_x) as price_x,
# -- TODO: After remaking retail view, replace with proper "TotalTHC"
# -- TODO: Replace with weighted average, w wts varied by inventorytype
# avg(thc + thca*0.877) as totalTHC,
# -- TODO: Replace this with a cleaned version of totalCBD? (
# avg(case when cbda is null then cbd
#      when cbda is not null then cbd + cbda * 0.877
#      end) as totalCBD
# 
# /*
# case when cbda is null then cbd
#      when cbda is not null then cbd + cbda * 0.877
#      end as totalCBD
# */
#       --avg(cbd + (if is not null cbda, cbda *0.877, 0)) as totalCBD
# FROM [full_WA_data__proper.Retail_ALL]
# GROUP BY invtype, YEAR, MONTH
# ORDER BY invtype, YEAR,MONTH

retailUSDxType <- read_csv("../gqoutput/results-20180627-174927.csv") %>%
  mutate(date=make_date(YEAR, MONTH)) %>%
  # Convert to $1000s
  mutate(price_x = price_x / 1e3) %>%
  filter(
    # remove NA
    !is.na(invtype),
    # remove non-retail products in here for no reason
    !invtype%in%c("Clone", "Mature Plant"),
    # Remove the partial month of October 2017
    date <= "2017-10-01")
```

#### Volume: Units, $ (x product type)

##### Sales Volume (Units)

```{r, echo=FALSE}
# TODO: Update query for proper unit/item-transaction definition
# Chart
retailUSDxType %>%
  ggplot(aes(x=date, y=itemtransactions, color=invtype)) + geom_line() +
  labs(title="Retail Item-Transactions by Inventory Type",
       y="Item-transactions (retail data rows)",
       x="") +
  theme_minimal() +
  scale_x_date(date_labels = "%b '%y", date_breaks="6 months")


# Table
retailUSDxType %>%
  select(invtype, date, itemtransactions) %>%
  spread(invtype, itemtransactions) %>%
  knitr::kable(caption='Retail Item-Transactions By Inventory Type', digits=0)

```

##### Sales Volume (Dollars)

```{r, echo=FALSE}
# Chart
retailUSDxType %>%
  ggplot(aes(x=date, y=price_x, color=invtype)) + geom_line() +
  labs(title="Gross Retail Sales by Inventory Type",
       y="$1000, Post-Excise",
       x="") +
  theme_minimal() +
  scale_x_date(date_labels = "%b '%y", date_breaks="6 months") +
  scale_y_continuous(labels=scales::dollar_format())


# Table
retailUSDxType %>%
  select(invtype, date, price_x) %>%
  spread(invtype, price_x) %>%
  knitr::kable(caption='Post-Excise Tax Sales By Inventory Type ($1k)', digits=0)

```


#### THC/CBD Content

```{r, echo=FALSE}
# TODO: Update query for weighted averages
# Chart
retailUSDxType %>%
  ggplot(aes(x=date, y=totalTHC, color=invtype)) + geom_line() +
  labs(title="THC Content by Inventory Type",
       y="THC Percent",
       x="") +
  theme_minimal() +
  scale_x_date(date_labels = "%b '%y", date_breaks="6 months")


# Table
retailUSDxType %>%
  select(invtype, date, totalTHC) %>%
  spread(invtype, totalTHC) %>%
  knitr::kable(caption='Mean THC Content By Inventory Type', digits=0)

```


```{r, echo=FALSE}
# TODO: Update query for weighted averages
# Chart
retailUSDxType %>%
  ggplot(aes(x=date, y=totalCBD, color=invtype)) + geom_line() +
  labs(title="CBD Content by Inventory Type",
       y="CBD Percent",
       x="") +
  theme_minimal() +
  scale_x_date(date_labels = "%b '%y", date_breaks="6 months")


# Table
retailUSDxType %>%
  select(invtype, date, totalCBD) %>%
  spread(invtype, totalCBD) %>%
  knitr::kable(caption='Mean CBD Content By Inventory Type', digits=0)

```

### Licensee Revenue Analysis

#### Producer/P&P/Processors

This can be generated from inventorytransfers table. inventorytransfer::saleprice. Validate/verify this. (5.3mil records)


```{r}
# GoogleQuery: ?????

# Aggregate revenues for all producers.

```

#### Stores

This can be generated from the dispensing table.

## Validation

Here are miscellaneous tables.

### Audit harvest v lots v conversion-parents

Lots are produced in the inventorycombinations table (from dry flower or OPM), before they then re-appear in the inventoryconversions table for conversions to other products. Therefore we can use these two tables (after cleaning) to validate the data. We will triangulate this from various tables:

+ inventorycombinations - lotting
+ inventoryconversions - parent product
+ inventoryconversions - child product

```{r}
lots %>% 
  group_by(NEWTYPE) %>%
  summarise(numlots = sum(numlots)) %>%
  kable(caption="Number of lots from inventorycombinations")
```

```{r}
convDetailed %>%
  filter(parent %in% c("Marijuana Mix", "Flower Lot", "Other Plant Material Lot")) %>%
  group_by(parent) %>%
  summarise(nConversions = sum(nConversions),
           parentwt = sum(parentwt, na.rm=T)) %>%
  arrange(-parentwt) %>%
  kable(caption='number of lots used as parent in inventoryconversions')
```

```{r}
convDetailed %>%
  filter(child %in% c("Marijuana Mix", "Flower Lot", "Other Plant Material Lot")) %>%
  group_by(child) %>%
  summarise(nConversions = sum(nConversions),
           childwt = sum(childwt, na.rm=T),
           childusablewt = sum(childusablewt, na.rm=T)) %>%
  arrange(-childwt) %>%
  kable(caption='number of lots used as child in inventoryconversions')
```

Though it is less interesting, we can also tabulate data by parent type. This can be used to validate.

### Validate Conversion-parents

This is not intrinsically interesting but could be used to validate harvest/lotting data. Note an average conversion-weight of almost 5000 (5kg?) for flower and 10,000 (10kg?) for OPM.

```{r}
convParent <- read_csv("../gqoutput/results-20180630-130516.csv") %>%
  mutate(inventorytype_parent = getInvtype(inventorytype_parent)) %>%
  mutate(wtPerConv = parentwt/nConversions) %>%
  arrange(-parentwt)
# -- QUERY
# SELECT inventorytype_parent,
#   count(*) as nConversions,
#   sum(CAST(parent_difference as integer)) as parentwt
# FROM [full_WA_data.biotrackthc_inventoryconversions]
# GROUP BY inventorytype_parent

knitr::kable(convParent, digits=1)
```